###Background
Here I process data

###Dataframe log
In this file I generate several versions of the phospho data through successive processing. They, in order:

phos_data_rawest: Raw data read directly from the file
phos_data_raw: Raw data with columns renamed, and genes and uniprots assigned
phos_data_raw_norm: Raw data normalised by median normalised
phos_data_raw_norm_filt1: Normalised raw data with non Class I sites filtered and extremely low intensity outliers filtered
phos_data_raw_norm_filt1_sum: phos_data_raw_norm_filt1 with summary statistics added



###Initialise
```{r}
library(tidyverse)
library(purrr)
library(ggplot2)
home_directory <- "..\\"
source(paste(home_directory, "scripts/essential_visualisations_JvG.R", sep = ""))
source(paste(home_directory, "scripts/boxplots_JvG.R", sep = ""))
source("..\\scripts/01_objects__1.R")
source("..\\scripts/02_global_functions__1.R")
source("scripts/02_basic_visualisations.R")
source("scripts/03_basic_functions.R")
source("scripts/04_processing.R")
```

###Load in data and rename columns
Rename info  cols
```{r}
#Load in
phos_data_rawest <- read.delim("data/raw/GxE_muscle_phos_phosdata_20220824_SH.txt")
phos_data_raw <- phos_data_rawest[-1, ]
#Make phos cols numerical
phos_cols <- grep("^X", colnames(phos_data_raw))
for (index in phos_cols){
  phos_data_raw[, index] <- as.numeric(phos_data_raw[, index])
}

#Rename info cols
phos_data_raw <- phos_data_raw %>%
  dplyr::select(-c(PTM.ModificationTitle,
            PTM.CollapseKey,
            PG.ProteinGroups)) %>%
  dplyr::rename(genes = PG.Genes,
         uniprots = PG.UniProtIds,
         protein = PTM.ProteinId,
         localisation_probability = Localization.probability,
         multiplicity = PTM.Multiplicity,
         AA = PTM.SiteAA,
         site_location = PTM.SiteLocation) %>%
  #Fix columns and make more names
  mutate(localisation_probability = as.numeric(localisation_probability),
         site = paste(AA, site_location, sep = ""))
```

Rename phospho cols using mouse UIDs (e.g. NOD_CHOW_ins_2)
```{r}
phos_colnames <- colnames(phos_data_raw)[grep("^X", colnames(phos_data_raw))]
#Load in pheno data to get UIDs
load("data/raw/sample_key__1.RData")
phos_colnames_mouse <- strsplit(phos_colnames, "_") %>%
  map(function(x){
    mouse <- rev(x)[1]
    mouse <- gsub("\\..+", "", mouse)
    return(mouse)
  }) %>% unlist
phos_colnames_UIDs <- map(phos_colnames_mouse,
                          function(x){
                            sample_key$UID[which(sample_key$Mouse == x)]
                          }) %>%
  unlist
names(phos_colnames_UIDs) <- phos_colnames
#Rename with UIDs
for (i in 1:length(phos_colnames_UIDs)){
  colnames(phos_data_raw)[which(colnames(phos_data_raw) ==
                                  names(phos_colnames_UIDs)[i])] <- phos_colnames_UIDs[i]
}

#Reorder so phoscols are in order and at the back
#Get ordered UIDs
UID_df <- strsplit(phos_colnames_UIDs, "_") %>%
  purrr::reduce(rbind) %>%
  as.data.frame()
colnames(UID_df) <- c("Strain", "Diet", "Ins", "num")
UID_df$UID <- phos_colnames_UIDs
UID_df <- mutate(UID_df,
                 Strain = factor(Strain, levels = Strain_levels),
                 Diet = factor(Diet, levels = Diet_levels),
                 Ins = factor(Ins, levels = Ins_levels),
                 num = as.numeric(num))
UID_df <- UID_df %>%
  .[order(.$Strain, .$Diet, .$Ins, .$num), ]
UIDs_ordered <- UID_df$UID
#Reorder
nonphos_colnames <- colnames(phos_data_raw)[which(colnames(phos_data_raw) %in%
                                                    phos_colnames_UIDs == FALSE)]
phos_data_raw <- phos_data_raw[, c(nonphos_colnames,
                                   UIDs_ordered)]
```

###Protein and gene naming
Assign uniprots and genes, and make names. Add sequence window
```{r}
#Assign uniprot by taking the assigned protein
phos_data_raw$uniprot <- phos_data_raw$protein

##Assign genes
#Take the gene that corresponds to the chosen uniprot
mult_genes_uniprots_df$uniprot_index <- map2(mult_genes_uniprots_df$uniprots,
                                             phos_data_raw$uniprot,
                                             function(choices, uniprot){which(choices == uniprot)}) %>%
  unlist
phos_data_raw$gene <- map2(mult_genes_uniprots_df$genes,
                           mult_genes_uniprots_df$uniprot_index,
                           function(choices, index){choices[index]}) %>%
  unlist
#For empty genes, turn them into the uniprot
no_gene_indices <- which(phos_data_raw$gene == "" |
                           is.na(phos_data_raw$gene))
phos_data_raw$gene[no_gene_indices] <- phos_data_raw$uniprot[no_gene_indices]

##Make standard name, uniprot_site, etc
#standard_name
phos_data_raw <- mutate(phos_data_raw,
                        standard_name = paste(gene, uniprot, site, multiplicity, sep = "_"))
rownames(phos_data_raw) <- phos_data_raw$standard_name
#All combinations of gene, uniprot, site, multiplicity
combs <- list(c(1, 2),
              c(1, 3),
              c(2, 3),
              c(3, 4),
              c(1, 2, 3))
names <- c("gene", "uniprot", "site", "multiplicity")
comb_colnames <- map(combs, ~paste(names[.], collapse = "_")) %>% unlist
phos_data_raw[, comb_colnames] <- map(combs,
                                      function(comb){
                                        map(strsplit(phos_data_raw$standard_name, "_"),
                                            ~paste(.[comb], collapse = "_")) %>% unlist
                                      }) %>%
  purrr::reduce(cbind)
#Add sequence window
uniprot_fastas <- read_fasta_to_list("data/intermediate/biol_databases/UP000000589_10090.fasta")
phos_data_raw$sequence_window <- map(phos_data_raw$uniprot_site,
                                     ~get_sequence_window(uniprot_fastas = uniprot_fastas,
                                                          uniprot_site = .)) %>% unlist
```


###Normalisation
```{r}
#normalise
phos_data_raw_norm <- median_normaliser("output/images/processing/normalisation/",
                                  phos_data_raw,
                                  num_cols = UIDs_ordered)
```



####Filtering
###Filtering by site score
```{r}
###Class 1 sites
#Reduce to just Class I (> 0.75)
phos_data_raw_norm_filt1 <- phos_data_raw_norm[which(phos_data_raw_norm$localisation_probability > 0.75), ]

###pheno_data
load("data/intermediate/pheno_data/pheno_data__5.RData")
num_cols <- colnames(phos_data_raw_norm_filt1) %>% .[grep("_\\d+$", .)]
non_num_cols <- setdiff(colnames(phos_data_raw_norm_filt1), num_cols)
num_cols <- num_cols %>% .[which(. %in% pheno_data$UID)]
phos_data_raw_norm_filt1 <- 
  phos_data_raw_norm_filt1[, which(colnames(phos_data_raw_norm_filt1) %in%
                                     c(num_cols, non_num_cols))]
#Update UIDs_ordered
UIDs_ordered_filtered <- intersect(UIDs_ordered, colnames(phos_data_raw_norm_filt1))
#Remove ppeptides that are now absent
filt1_quant_vec <- rowSums(!is.na(phos_data_raw_norm_filt1[, UIDs_ordered_filtered]))
phos_data_raw_norm_filt1 <- phos_data_raw_norm_filt1[which(filt1_quant_vec > 0), ]
```

###Filtering out low intensity values
There are some extremely low intensity values (log2 < 5) that generally seem like outliers, in that they appear in sites that are otherwise quantified in many samples with much higher intensity. Here I filter those out
```{r}
###Filter sites with log2 int < 5 and > 6 from ppeptide median
#This was determined through analysis in 11_low_intensity_values.Rmd
source("scripts/07_filtering.R")
lowint_filter_df <-  filter_low_and_belowbulk(phos_data_raw_norm_filt1,
                                     num_cols = UIDs_ordered_filtered,
                                     threshold_low = 5,
                                     threshold_diff = 6)
lowint_filter_m <- as.matrix(lowint_filter_df[, -ncol(lowint_filter_df)])
phos_data_raw_norm_filt1[, UIDs_ordered_filtered][lowint_filter_m] <- NA
```


###Summary stats
```{r}
#Medians and median FCs. Means
phos_data_raw_norm_filt1_sum <- GxEphos_mean_FC_maker(phos_data_raw_norm_filt1,
                                   summary_fun = "median",
                                   num_cols = UIDs_ordered_filtered)
means <- condition_averager(phos_data_raw_norm_filt1,
                   summary_fun = "mean",
                   num_cols = UIDs_ordered_filtered)
phos_data_raw_norm_filt1_sum <- cbind(phos_data_raw_norm_filt1_sum, means)
#Ins response
ins_response <- GxEphos_insresponse_maker(phos_data_raw_norm_filt1,
                          num_cols = UIDs_ordered_filtered,
                          summary_func = function(x){median(x, na.rm = TRUE)})
phos_data_raw_norm_filt1_sum <- cbind(phos_data_raw_norm_filt1_sum, ins_response)
#CV
phos_data_raw_norm_filt1_sum <- GxEphos_CVs(phos_data_raw_norm_filt1_sum,
                                            num_cols = UIDs_ordered_filtered)

#Number of quantified replicates
phos_data_raw_norm_filt1_sum <- GxEphos_quant_calculator(phos_data_raw_norm_filt1_sum,
                                            num_cols = UIDs_ordered_filtered)
```



###QC
Quantification, PCA, correlation, hierarchical clustering
```{r}
#Set up
source("scripts/01_QC.R")
QC_data <- phos_data_raw_norm_filt1_sum
num_cols <- UIDs_ordered_filtered


###Quantification
##Per sample
quant_df <- quant_df_maker(data = QC_data,
                           num_cols = num_cols)
quant_obs <- c("Phosphopeptides" = "ppeptides",
               "Phosphosites" = "psites",
               "Phosphoproteins" = "pproteins")
map2(quant_obs, names(quant_obs),
     function(ob, name){
       quant_barplot(quant_df,
              ycol = name,
              file = paste("output/images/QC/quant/bplot_quant_",
                           ob,
                           "_persample",
                           sep = ""))
     })
#Numbers
quant_df["total", ]
apply(quant_df[-nrow(quant_df), 1:3], 2, FUN = "mean")

##Ppeptide hist
quant_histogram <- quant_hist(data = QC_data,
                             num_cols = num_cols)
quant_histogram
ggsave_pdfpng("output/images/QC/quant/hgram_quant_perppeptide",
              width = 2, height = 1.5)
##Upset plot for ppeptides quantified in each strain
quant_condition_df <- quant_condition_df_maker(QC_data,
                                               num_cols,
                                               c("Strain", "StrainDiet", "StrainDietIns"))
Strain_quant_upset <- upset_plot(quant_condition_df,
                                 upset_list_col = "quant_Strain_list",
                                 ylab = "Phosphopeptides")
save_pdfpng(Strain_quant_upset, "output/images/QC/quant/upsetplot_Strainquant",
              width = 4, height = 2)

##Number of ppeptides quantified in only one strain
quant_df_onestrain <- data.frame("Strain" = factor(all_levels$Strain,
                                                   levels = all_levels$Strain)) %>%
  mutate(num_ppeptides = map(Strain, function(strain){
    length(which(quant_condition_df$quant_Strain == strain))
  }) %>% unlist)
#plot
ggplot(quant_df_onestrain, aes(x = Strain, y = num_ppeptides)) +
  geom_col(fill = "black", width = 0.8) +
  comfy_theme(include_xaxis = FALSE,
              rotate_x_text = TRUE) +
  theme(axis.title.x = element_blank()) +
  labs(y = "Phosphopeptides")
ggsave_pdfpng("output/images/QC/quant/barplot_Strainspecific_quant",
              width = 1.25, height = 1.5)

###PCA
PC_combos <- list(c(1, 2),
                  c(2, 3),
                  c(3, 4))
map(PC_combos,
    function(PCs){
      pca_plot_output <- pca_plot(data = QC_data,
                            num_cols = num_cols,
                            PCs = PCs)
      pca_plot_output
      ggsave_pdfpng(paste("output/images/QC/cluster/pplot_PCA",
                          PCs[1],
                          PCs[2],
                          sep = "_"),
                    width = 2.5, height = 1.5)
    })

###Correlation heatmap
corr_m_list <- corr_m_maker(QC_data, num_cols)
pdf("output/images/QC/cluster/hmap_sample_corrs.pdf",
    width = 4, height = 4)
corr_m_plotter(corr_m_list$corr_m,
               black_fraction = 17,
               total_fraction = 20,
               text_size = 0.2*7/6)
dev.off()

###Clustered dendogram
#Set up colours
colour_ns <- map(Strain_levels, ~length(grep(., num_cols))) %>% unlist
dend_colours <- map2(fivestraincols_main, colour_ns,
                      function(col, n) rep(col, n)) %>% unlist
#Dendogram
h_dend <- clustered_dendogram(QC_data,
                              num_cols = num_cols,
                              colours = dend_colours)
pdf("output/images/QC/cluster/dendogram_clustering.pdf",
    width = 4.5, height = 3)
plot(h_dend,
     main = "Hierarchical clustering")
dev.off()
```


###Output
```{r}
save(phos_data_raw_norm_filt1_sum,
     file = "output/data/phos_data_raw_norm_filt1_sum__1.RData")
phos_data_proc <- phos_data_raw_norm_filt1_sum
save(phos_data_proc,
     file = "output/data/phos_data_proc__1.RData")
phos_num_cols <- UIDs_ordered_filtered
save(phos_num_cols,
     file = "output/data/phos_num_cols__1.RData")
```










