###Background
Here I search for and characterise insulin-regulated sites. I also assess how they are affected by strain and/or diet

###Initialise
```{r}
library(tidyverse)
library(purrr)
library(ggplot2)
library(qvalue)
home_directory <- "..\\"
source(paste(home_directory, "scripts/essential_visualisations_JvG.R", sep = ""))
source(paste(home_directory, "scripts/boxplots_JvG.R", sep = ""))
source(paste(home_directory, "scripts/stats_JvG.R", sep = ""))
source(paste(home_directory, "scripts/enrichment_analysis_JvG.R", sep = ""))
source("..\\scripts/01_objects__1.R")
source("..\\scripts/02_global_functions__1.R")
source("scripts/02_basic_visualisations.R")
source("scripts/03_basic_functions.R")
source("scripts/06_annotation.R")
source("scripts/08_ins_reg.R")
```

###Load and prep data
```{r}
load("data/intermediate/phos_data/phos_data_proc__1.RData")
load("data/intermediate/phos_data/annotation/phos_data_annotation__1.RData")
load("data/intermediate/phos_data/phos_num_cols__1.RData")
#Number of quantified samples per ppeptide in each condition
phos_quant_df <- condition_quanter(phos_data_proc)

phos_data_proc_insreg <- phos_data_proc

phos_num_cols_basnorm <- colnames(phos_data_proc_insreg)[grep("basnorm_\\d+", 
                                                              colnames(phos_data_proc_insreg))]
```


####Stats for insulin regulation and differences in insulin regulation

###Insreg stats
```{r}
##Set up
filter_args <- map(all_levels$StrainDiet,
                         ~list("bas_quant" = phos_quant_df[, paste(., "_bas", sep = "")],
                               "ins_quant" = phos_quant_df[, paste(., "_ins", sep = "")]))
names(filter_args) <- all_levels$StrainDiet 
filter_func <- function(args){basins_quant_StrainDietfilter(args = args,
                                                            bas_threshold = 3,
                                                            ins_threshold = 3)}
StrainDiet_threshold <- 8
data <- phos_data_proc_insreg

##StrainDiet filter
data_filtered <- apply_StrainDietfilter(filter_func = filter_func,
                                                arguments = filter_args,
                                                ppeptides = rownames(data),
                                        StrainDiet_threshold = StrainDiet_threshold)
#Make NAs in data for StrainDiets that do not pass the filter
num_cols_forNA <- c(phos_num_cols_basnorm,
                    all_FC_cols$Ins,
                    phos_num_cols)
NA_data <- StrainDiet_filter_makeNAs(filter_df = data_filtered[, all_levels$StrainDiet],
                                     num_df = data[, num_cols_forNA])
data_wNAs <- data
data_wNAs[, num_cols_forNA] <- NA_data
#Restrict to just sites that pass combined filter
data_wNAs_filt <- data_wNAs[data_filtered$combined, ]
##Insreg stats
test_results <- ppeptide_stat_runner(data_wNAs_filt, 
                          test_func = ins_3wayaov, num_cols = phos_num_cols)

#Map back into data_wNAs_filt
data_wNAs_filt[, c("ins3wayaovint_p", "ins3wayaovint_F")] <- test_results[, c("p", "F")]
#Insreg filtering
data_insreg_list <- insreg_FC_filterer_directedMax(data_wNAs_filt,
                               FC_cutoff = 0.58,
                               FC_columns = all_FC_cols$Ins,
                               q_cutoff = 0.05,
                               q_col = NULL,
                               p_col = "ins3wayaovint_p",
                               suffix = NULL)
#Map into data_wNAs_filt and phos_data_proc_insreg
data_wNAs_filt <- data_insreg_list$data
phos_data_proc_insreg <- map_data_into_larger(data_source = data_wNAs_filt,
                                              data_target = phos_data_proc_insreg,
                                              cols_to_map = c("ins3wayaovint_p", "ins3wayaovint_F",
                                                              "ins3wayaovint_q",
                                                              "ins_bas_logFC_StrainDietmax",
                                                              "insreg_bool", "insreg_dir"),
                                              factors_to_preserve = list(c("insreg_dir", "unregulated")))
phos_data_proc_insreg$insreg_tested <- rownames(phos_data_proc_insreg) %in%
  rownames(data_wNAs_filt)
```

###Strain differences in CHOW mice
Here I run a one-way ANOVA (ins resp ~ Strain) in CHOW mice and perform post-hoc tests to identify where insulin regulation differs in strains compared to C57Bl6J
```{r}
#Subset data_wNAs_filt for insulin-regulated sites
insreg_data <- subset(data_wNAs_filt, insreg_bool == TRUE)
##Run ANOVAs
data_CHOWaov <- ppeptide_stat_runner(insreg_data,
                                 num_cols = phos_num_cols_basnorm[grep("CHOW", phos_num_cols_basnorm)],
                                 test_func = strain_CHOW_aov,
                                 results_format = c("p", "F"))

#Adjust pvals
hist(data_CHOWaov$p)
data_CHOWaov$q <- qvalue(data_CHOWaov$p)$qvalues
data_CHOWaov$sig <- data_CHOWaov$q < 0.05
colnames(data_CHOWaov) <- paste("Strainaov_", colnames(data_CHOWaov), sep = "")

##Posthoc tests
#Set up
comparisons <- paste(all_levels$Strain[all_levels$Strain != "C57Bl6J"], "_vs_C57Bl6J", sep = "")
results_cols <- cross(list(c("p", "t"), comparisons)) %>%
  map(~paste(rev(unlist(.)), collapse = "_")) %>% unlist
test_func <- Strain_C57Bl6J_ttests
ppeptides <- rownames(subset(data_CHOWaov, Strainaov_sig == TRUE))
#Run ttests
data_CHOWaov_phoc <- ppeptide_stat_runner(insreg_data[ppeptides, ],
                             num_cols = phos_num_cols_basnorm[grep("CHOW", phos_num_cols_basnorm)],
                             test_func = test_func,
                             results_format = results_cols)
#Adjust pvalues
data_CHOWaov_phoc <- qval_adjustment_mult_groupcols(data_CHOWaov_phoc, 
                                              pcols = colnames(data_CHOWaov_phoc)[grep("_p$",
                                                                                 colnames(data_CHOWaov_phoc))])

##Run FC filtering
#Add relevant FC columsn
FC_cols <- all_FC_cols$Ins[grep("CHOW", all_FC_cols$Ins)]
data_CHOWaov_phoc[, FC_cols] <- insreg_data[rownames(data_CHOWaov_phoc), FC_cols]
#Set up FC comparisons
Strains_noB6 <- all_levels$Strain[all_levels$Strain != "C57Bl6J"]
names(Strains_noB6) <- Strains_noB6
totest_list <- map(Strains_noB6, 
                   ~data_CHOWaov_phoc[, paste(., "_vs_C57Bl6J_sig", sep = "")])
testFC_list <- map(Strains_noB6, 
                   ~data_CHOWaov_phoc[, paste(., "_CHOW_bas_vs_", ., "_CHOW_ins_logFC", sep = "")])
CTRLFC_list <- map(Strains_noB6, ~data_CHOWaov_phoc$C57Bl6J_CHOW_bas_vs_C57Bl6J_CHOW_ins_logFC)
#Run comparisons
FC_comparisons <- FC_comparer(totest_list = totest_list,
                              testFC_list = testFC_list,
                              CTRLFC_list = CTRLFC_list,
                              FC_comp_func = FC_filter_adaplin)
data_CHOWaov_phoc <- cbind(data_CHOWaov_phoc, FC_comparisons)
#Summarise changed Strains
data_CHOWaov_phoc$change_conds <- 
  map(1:nrow(data_CHOWaov_phoc),
      function(index){
        changed_bool <- as.logical(data_CHOWaov_phoc[index, paste(Strains_noB6,
                                                              "_change_bool", sep = "")])
        changed_Strains <- Strains_noB6[changed_bool]
        pasted_Strains <- paste(changed_Strains, collapse = ";")
        if (pasted_Strains == ""){pasted_Strains <- NA}
        return(pasted_Strains)
      }) %>% unlist
data_CHOWaov_phoc$change_bool <- !is.na(data_CHOWaov_phoc$change_conds)
data_CHOWaov_phoc$change_num <- map(strsplit(data_CHOWaov_phoc$change_conds, ";"), 
                                    function(vec){
                                      if (is.na(vec[1])){
                                        return(0)
                                      } else {
                                        return(length(vec))
                                      }
                                    }) %>% unlist
data_CHOWaov_phoc <- mutate(data_CHOWaov_phoc, 
                            change_num = factor(change_num, levels = sort(unique(change_num))))

##Call differences as enhanced or suppressed
#enhsupp in individual conditions
data_CHOWaov_phoc$insreg_dir <- phos_data_proc_insreg[rownames(data_CHOWaov_phoc), "insreg_dir"]
data_CHOWaov_phoc <- enhsupp_insreg_caller(data_CHOWaov_phoc,
                                           colnames(data_CHOWaov_phoc)[grep("change_dir$", 
                                                                            colnames(data_CHOWaov_phoc))])
#enhsupp overall
data_CHOWaov_phoc$change_enhsupp <- enhsupp_combiner(data_CHOWaov_phoc,
                                                    columns = colnames(data_CHOWaov_phoc)[grep("enhsupp$",
                                                                                               colnames(data_CHOWaov_phoc))])

##Rename and map back in to data_wNAs_filt and phos_data_proc_insreg
#Remove columns
data_CHOWaov_phoc_mapping <- data_CHOWaov_phoc
data_CHOWaov_phoc_mapping <- data_CHOWaov_phoc_mapping[, -c(grep("logFC", colnames(data_CHOWaov_phoc_mapping)),
                                            grep("insreg_dir", colnames(data_CHOWaov_phoc_mapping)))]
#Rename
colnames(data_CHOWaov_phoc_mapping) <- paste("insregdiff_StrainCHOW_", 
                                             colnames(data_CHOWaov_phoc_mapping), sep = "")
#Map back in
data_wNAs_filt <- map_data_into_larger(data_source = data_CHOWaov,
                                       data_target = data_wNAs_filt,
                                       cols_to_map = colnames(data_CHOWaov))
data_wNAs_filt <- map_data_into_larger(data_source = data_CHOWaov_phoc_mapping,
                                       data_target = data_wNAs_filt,
                                       cols_to_map = colnames(data_CHOWaov_phoc_mapping),
                                       factors_to_preserve = list(c("insregdiff_StrainCHOW_change_num",
                                                               0)))
phos_data_proc_insreg <- map_data_into_larger(data_source = data_CHOWaov_phoc_mapping,
                                       data_target = phos_data_proc_insreg,
                       cols_to_map = c("insregdiff_StrainCHOW_change_bool",
                                       "insregdiff_StrainCHOW_change_conds",
                                       "insregdiff_StrainCHOW_change_num",
                                       colnames(data_CHOWaov_phoc_mapping)[grep("enhsupp$",
                                                                                colnames(data_CHOWaov_phoc_mapping))]),
                       factors_to_preserve = list(c("insregdiff_StrainCHOW_change_num",
                                                               0)))
```



###Diet and StrainxDiet effects
Anova and ttests
```{r}
##Anova
data_Diet_SxDaov <- insregdiff_Diet_strainxdiet_aov(data_insreg_list$data_insreg)
##ttests for StrainxDiet
diet_comparisons <- map(all_levels$Strain, ~paste(., "_HFD_vs_", ., "_CHOW", sep = "")) %>% unlist
results_cols <- cross(list(c("p", "t"), diet_comparisons)) %>%
  map(~paste(rev(unlist(.)), collapse = "_")) %>% unlist
test_func <- StrainxDiet_Diet_ttests
ppeptides <- rownames(subset(data_Diet_SxDaov, posthoc_class == "StrainxDiet"))
#Run ttests
data_Diet_SxDaov_SxDttests <- ppeptide_stat_runner(data_wNAs_filt[ppeptides, ],
                             num_cols = phos_num_cols_basnorm,
                             test_func = test_func,
                             results_format = results_cols)
#Adjust pvalues
data_Diet_SxDaov_SxDttests <- qval_adjustment_mult_groupcols(data_Diet_SxDaov_SxDttests,
                                                             pcols = results_cols[grep("_p$",
                                                                                       results_cols)])
```

FC filtering
```{r}
###StrainxDiet
data_tested <- data_Diet_SxDaov_SxDttests
##FC filtering
#Add relevant FCs
data_tested[, all_FC_cols$Ins] <- data_wNAs_filt[rownames(data_tested), all_FC_cols$Ins]
#Set up FC comparisons
names(diet_comparisons) <- diet_comparisons
totest_list <- map(diet_comparisons, 
                   ~data_tested[, paste(., "_sig", sep = "")])
testFC_list <- strsplit(diet_comparisons, "_vs_") %>% map(function(list){
  StrainDiet <- list[1]
  FC_col <- paste(StrainDiet, "_bas_vs_", StrainDiet, "_ins_logFC", sep = "")
  return(data_tested[, FC_col])
})
CTRLFC_list <- strsplit(diet_comparisons, "_vs_") %>% map(function(list){
  StrainDiet <- list[2]
  FC_col <- paste(StrainDiet, "_bas_vs_", StrainDiet, "_ins_logFC", sep = "")
  return(data_tested[, FC_col])
})
#Run comparisons
FC_comparisons <- FC_comparer(totest_list = totest_list,
                              testFC_list = testFC_list,
                              CTRLFC_list = CTRLFC_list,
                              FC_comp_func = FC_filter_adaplin)
data_tested <- cbind(data_tested, FC_comparisons)
#Summarise changed conditions
data_tested$change_conds <- 
map(1:nrow(data_tested),
    function(index){
      changed_bool <- as.logical(data_tested[index, paste(diet_comparisons,
                                                            "_change_bool", sep = "")])
      Strains <- strsplit(diet_comparisons, "_") %>% map(~.[1]) %>% unlist
      changed_Strains <- Strains[changed_bool]
      pasted_Strains <- paste(changed_Strains, collapse = ";")
      if (pasted_Strains == ""){pasted_Strains <- NA}
      return(pasted_Strains)
    }) %>% unlist
data_tested$change_bool <- !is.na(data_tested$change_conds)
data_tested$change_num <- map(strsplit(data_tested$change_conds, ";"), 
                                    function(vec){
                                      if (is.na(vec[1])){
                                        return(0)
                                      } else {
                                        return(length(vec))
                                      }
                                    }) %>% unlist 
data_tested <- mutate(data_tested, change_num = factor(change_num,
                                                       levels = sort(unique(change_num))))
#Rename
data_Diet_SxDaov_SxDFCfilt <- data_tested
colnames(data_Diet_SxDaov_SxDFCfilt) <- paste("StrainxDiet_", colnames(data_Diet_SxDaov_SxDFCfilt), sep = "")

###Diet
data_tested <- subset(data_Diet_SxDaov, posthoc_class == "Diet")
##Calculate FCs
#Mean of ins/bas in each diet
data_wNAs_filt$CHOW_bas_vs_CHOW_ins <- apply(data_wNAs_filt[, all_FC_cols$Ins[grep("CHOW", all_FC_cols$Ins)]],
                                        1, FUN = mean, na.rm = TRUE)
data_wNAs_filt$HFD_bas_vs_HFD_ins <- apply(data_wNAs_filt[, all_FC_cols$Ins[grep("HFD", all_FC_cols$Ins)]],
                                        1, FUN = mean, na.rm = TRUE)
FC_cols <- c("CHOW_bas_vs_CHOW_ins", "HFD_bas_vs_HFD_ins")
data_tested[, FC_cols] <- data_wNAs_filt[rownames(data_tested), FC_cols]
data_tested <- data_tested[, FC_cols]
##Set up FC comparisons
#This is specific to Strain
totest_list <- list("diet" = rep(TRUE, nrow(data_tested)))
testFC_list <- list("diet" = data_tested$HFD_bas_vs_HFD_ins)
CTRLFC_list <- list("diet" = data_tested$CHOW_bas_vs_CHOW_ins)

#Run comparisons
FC_comparisons <- FC_comparer(totest_list = totest_list,
                              testFC_list = testFC_list,
                              CTRLFC_list = CTRLFC_list,
                              FC_comp_func = FC_filter_adaplin)
data_tested <- cbind(data_tested, FC_comparisons)
#Rename
data_Diet_SxDaov_DFCfilt <- data_tested
colnames(data_Diet_SxDaov_DFCfilt) <- paste("Diet_", colnames(data_Diet_SxDaov_DFCfilt), sep = "")
colnames(data_Diet_SxDaov_DFCfilt) <- gsub("Diet_diet_", "Diet_", colnames(data_Diet_SxDaov_DFCfilt))
```

Combine StrainxDiet and Diet results and map back
```{r}
##Combine anova results, SxD filtering results, and D filtering results
data_Diet_SxDaov_comb <- data_Diet_SxDaov
colnames(data_Diet_SxDaov_comb) <- paste("SxDaov_", colnames(data_Diet_SxDaov_comb), sep = "")
data_Diet_SxDaov_comb <- map_data_into_larger(data_source = data_Diet_SxDaov_SxDFCfilt,
                                              data_target = data_Diet_SxDaov_comb,
                                              cols_to_map =  colnames(data_Diet_SxDaov_SxDFCfilt))
data_Diet_SxDaov_comb <- map_data_into_larger(data_source = data_Diet_SxDaov_DFCfilt,
                                              data_target = data_Diet_SxDaov_comb,
                                              cols_to_map =  colnames(data_Diet_SxDaov_DFCfilt))
##Enhsupp
#Map in insreg
data_Diet_SxDaov_comb$insreg_dir <- phos_data_proc_insreg[rownames(data_Diet_SxDaov_comb), "insreg_dir"]
data_Diet_SxDaov_comb <- enhsupp_insreg_caller(data_Diet_SxDaov_comb,
                                               insregdiff_dir_cols = 
                                                 colnames(data_Diet_SxDaov_comb)[grep("change_dir",
                                                                                      colnames(data_Diet_SxDaov_comb))])
data_Diet_SxDaov_comb$StrainxDiet_change_enhsupp <- 
  enhsupp_combiner(data_Diet_SxDaov_comb,
                   columns = colnames(data_Diet_SxDaov_comb)[intersect(grep("^StrainxDiet",
                                                                            colnames(data_Diet_SxDaov_comb)),
                                                                       grep("enhsupp$", 
                                                                            colnames(data_Diet_SxDaov_comb)))])
##Add overall Diet effect columns
data_Diet_SxDaov_comb$Dietoverall_change_bool <- data_Diet_SxDaov_comb$StrainxDiet_change_bool |
  data_Diet_SxDaov_comb$Diet_change_bool
data_Diet_SxDaov_comb$Dietoverall_change_enhsupp <- 
  enhsupp_combiner(data_Diet_SxDaov_comb, columns = 
                     c(colnames(data_Diet_SxDaov_comb)[intersect(grep("^StrainxDiet",
                                                            colnames(data_Diet_SxDaov_comb)),
                                                       grep("CHOW_change_enhsupp$", 
                                                            colnames(data_Diet_SxDaov_comb)))],
                       "Diet_change_enhsupp"))
##Rename and add to data_wNAs_filt and phos_data_proc_insreg
colnames(data_Diet_SxDaov_comb) <- paste("insregdiff_", colnames(data_Diet_SxDaov_comb), sep = "")
data_wNAs_filt <- map_data_into_larger(data_source = data_Diet_SxDaov_comb,
                                       data_target = data_wNAs_filt,
                                       cols_to_map = colnames(data_Diet_SxDaov_comb),
                                       factors_to_preserve = list(c("insregdiff_StrainxDiet_change_num",
                                                                    0)))
phos_data_proc_insreg <- map_data_into_larger(data_source = data_Diet_SxDaov_comb,
                                       data_target = phos_data_proc_insreg,
     cols_to_map = c("insregdiff_StrainxDiet_change_bool",
                     "insregdiff_StrainxDiet_change_conds",
                     "insregdiff_StrainxDiet_change_num",
                     colnames(data_Diet_SxDaov_comb)[intersect(grep("^insregdiff_StrainxDiet",
                                                                    colnames(data_Diet_SxDaov_comb)),
                                                               grep("enhsupp$", 
                                                                    colnames(data_Diet_SxDaov_comb)))],
                     "insregdiff_Diet_change_bool",
                     "insregdiff_Diet_change_dir",
                     "insregdiff_Diet_change_enhsupp",
                     "insregdiff_Dietoverall_change_bool",
                     "insregdiff_Dietoverall_change_enhsupp"),
                                       factors_to_preserve = list(c("insregdiff_StrainxDiet_change_num",
                                                                    0)))
```

###Combining Strain and Diet analysis
```{r}
##For each ppetpide: Is there S, D, and/or SxD effect?
factors <- c("Strain" = "insregdiff_StrainCHOW_change_bool",
                "Diet" = "insregdiff_Diet_change_bool",
                "StrainxDiet" = "insregdiff_StrainxDiet_change_bool")
phos_data_proc_insreg$insregdiff_change_factors <- map(1:nrow(phos_data_proc_insreg), function(index){
  bool_vec <- as.logical(phos_data_proc_insreg[index, factors])
  changed_factors <- names(factors)[bool_vec]
  pasted_factors <- paste(changed_factors, collapse = ";")
  if (pasted_factors == ""){
    pasted_factors <- NA
  }
  return(pasted_factors)
}) %>% unlist
phos_data_proc_insreg <- mutate(phos_data_proc_insreg,
                                insregdiff_change_factors = factor(insregdiff_change_factors,
                                                                   levels = c("Strain",
                                                                              "Diet",
                                                                              "StrainxDiet",
                                                                              "Strain;Diet",
                                                                              "Strain;StrainxDiet")))
phos_data_proc_insreg$insregdiff_change_bool <- !is.na(phos_data_proc_insreg$insregdiff_change_factors)
```


###Summarise insulin regulation and insreg differences

Filtering process from all ppeptides to insreg differences
```{r}
phos_data_proc_insreg$ins3wayaovint_sig <- phos_data_proc_insreg$ins3wayaovint_q < 0.05
summary_filtering_vec <- colSums(phos_data_proc_insreg[, c("insreg_tested",
                                                           "ins3wayaovint_sig",
                                  "insreg_bool",
                                  "insregdiff_change_bool")], na.rm = TRUE)
summary_filtering <- data.frame("level" = names(summary_filtering_vec),
                                "Freq" = summary_filtering_vec)
summary_filtering <- rbind(c("quantified", nrow(phos_data_proc_insreg)),
                           summary_filtering)
rownames(summary_filtering) <- summary_filtering$level
```

Summarise up and down
```{r}
###Summary of up, down, enh, supp, by Strain, Diet, StrainxDiet
##Make summary

types <- c("Strain", "Diet", "StrainxDiet")
cols <- c("insregdiff_StrainCHOW_change_enhsupp",
          "insregdiff_Diet_change_enhsupp",
          "insregdiff_StrainxDiet_change_enhsupp")
names(cols) <- types
summary_list <- map(types, function(type){
  #Set up column
  col <- cols[type]
  #Reduce data 
  data <- phos_data_proc_insreg[!is.na(phos_data_proc_insreg[, col]), ]
  data[, col] <- factor(data[, col],
                                  levels = c("enhanced", "suppressed", "enhanced;suppressed"))
  #Get summary
  summary_df <- table(data[, col], data$insreg_dir) %>% as.data.frame 
  summary_df <- dplyr::rename(summary_df,
                       enhsupp = Var1, insreg_dir = Var2) %>%
    subset(insreg_dir != "unregulated")
  summary_df$type <- type
  return(summary_df)
})
#Overall summary of insulin regulation
insreg_summary <- table(phos_data_proc_insreg$insreg_dir) %>% as.data.frame %>%
  dplyr::rename(insreg_dir = Var1) %>% subset(insreg_dir != "unregulated") %>%
  mutate(enhsupp = "enhanced;suppressed", type = "Total", insreg_dir = as.character(insreg_dir)) %>%
  .[, colnames(summary_list[[1]])]
#Combine
summary_df <- purrr::reduce(summary_list, rbind) %>%
  mutate(enhsupp = as.character(enhsupp),
         insreg_dir = as.character(insreg_dir))
summary_df <- rbind(summary_df, insreg_summary) %>%
  #Make factors and add columns
  mutate(enhsupp = factor(enhsupp, levels = c("enhanced", "enhanced;suppressed", "suppressed")),
         insreg_dir = factor(insreg_dir, levels = c("up", "down")),
         type = factor(type, levels = c("Total", "Strain", "Diet", "StrainxDiet"))) %>%
  .[order(.$insreg_dir, .$enhsupp), ] %>%
  mutate(insregdir_enhsupp = paste(insreg_dir, enhsupp, sep = "_")) %>%
  mutate(insregdir_enhsupp = factor(insregdir_enhsupp, levels = unique(insregdir_enhsupp)))
#Reorder
summary_df <- summary_df %>% .[order(.$type, .$insreg_dir, .$enhsupp), ]
#Output
updown_enhsupp_summary <- summary_df
```

Summary of S, D, SxD, and combinations
```{r}
#Make summary
insregdiff_combs_summary <- summariser_twoway(phos_data_proc_insreg,
                                              Var1 = "insregdiff_change_factors",
                                              Var2 = "insreg_dir") %>%
  subset(insregdiff_change_factors != "total" &
           insreg_dir != "total" &
           insreg_dir != "unregulated")
#Add total insreg
insreg_summary <- table(phos_data_proc_insreg$insreg_dir) %>% as.data.frame %>%
  dplyr::rename(insreg_dir = Var1) %>% subset(insreg_dir != "unregulated") %>%
  mutate(insregdiff_change_factors = "Total") %>%
  .[, colnames(insregdiff_combs_summary)]
#Combine
insregdiff_combs_summary <- mutate(insregdiff_combs_summary,
                                   insregdiff_change_factors = 
                                     factor(insregdiff_change_factors,
                                            levels = c("Total", "Strain", "Diet", "StrainxDiet",
                                                       "Strain;Diet", "Strain;StrainxDiet"))) %>%
  rbind(insreg_summary) %>%
  mutate(insreg_dir = factor(insreg_dir, levels = c("up", "down"))) %>%
  dplyr::rename(type = insregdiff_change_factors) %>%
  .[order(.$type), ]
```

Summary of S and SxD distrubitions across strains
```{r}
#Strain
insregdiffStrain_summary <- list(
    "Strains" = insregdiff_strains_summariser(phos_data_proc_insreg,
                                              strains = all_levels$Strain[all_levels$Strain != "C57Bl6J"],
                                              "insregdiff_StrainCHOW_BLANK_change_enhsupp"),
  "Combs" = insregdiff_combs_summariser(phos_data_proc_insreg,
                                                        "insregdiff_StrainCHOW_change_conds",
                                                        "insregdiff_StrainCHOW_BLANK_change_enhsupp")
)

#StrainxDiet
insregdiffStrainxDiet_summary <- list(
  "Strains" = insregdiff_strains_summariser(phos_data_proc_insreg,
                                            strains = all_levels$Strain,
                                            "insregdiff_StrainxDiet_BLANK_HFD_vs_BLANK_CHOW_change_enhsupp"),
  "Combs" = insregdiff_combs_summariser(phos_data_proc_insreg,
                                                        "insregdiff_StrainxDiet_change_conds",
                                                        "insregdiff_StrainxDiet_BLANK_HFD_vs_BLANK_CHOW_change_enhsupp")
)
```

Combine all summaries and output
```{r}
summaries_list <- list(
  "filtering" = summary_filtering,
  "overall_updown_enhsupp" = updown_enhsupp_summary,
  "overall_updown_enhsupp_combinations" = insregdiff_combs_summary,
  "Strain_diffs_strains_and_combs" = insregdiffStrain_summary,
  "StrainxDiet_diffs_strains_and_combs" = insregdiffStrainxDiet_summary
)
save(summaries_list, file = "output/data/analysis/insulin_regulation/summaries_list__2.RData")
```


###Visualise summaries

Barplots
```{r}
insresp_dir <- "output/images/analysis/insulin_regulation/insreg_changes/"
##Overall insreg and S, D, SxD differences
#Barplot for reg, S, D, SxD overall
insreg_barplot_3cols(updown_enhsupp_summary, x_aes = "type",
                     filename = paste(insresp_dir, 
                                      "CHOW_Strain_aov/summary/barplot_insregdif", sep = ""),
                     width = 2.25, height = 2)

###Distributions of Strain and StrainxDiet differences
##Strain
Strain_StrainxDiet_bplot_args <- list(
  "combs" = list("x_aes" = "combination", "list_arg" = "Combs",
                 "width" = 3.5, height = 2),
  "numconds" = list("x_aes" = "num_conds", "list_arg" = "Combs",
                 "width" = 2.25, height = 2),
  "strains" = list("x_aes" = "Strain", "list_arg" = "Strains",
                 "width" = 2.25, height = 2)
)
map2(Strain_StrainxDiet_bplot_args, names(Strain_StrainxDiet_bplot_args),
     function(args, name){
       #Strain
       insreg_barplot_3cols(insregdiffStrain_summary[[args$list_arg]], x_aes = args$x_aes,
                     filename = paste(insresp_dir, 
                                      "CHOW_Strain_aov/summary/barplot_insregdiffStrain_",
                                      name,
                                      sep = ""),
                     width = args$width, height = args$height)
       #StrainxDiet
       insreg_barplot_3cols(insregdiffStrainxDiet_summary[[args$list_arg]], x_aes = args$x_aes,
                     filename = paste(insresp_dir, 
                                      "Diet_2wayaov/summary//barplot_insregdiffStrainxDiet_",
                                      name,
                                      sep = ""),
                     width = args$width, height = args$height)
     })
```



####Visualisations
##Global visualisations 
Heatmaps
ins/bas
```{r}
##Strain differences
heatmap_GxEphos_clustered(data = subset(phos_data_proc_insreg, insregdiff_StrainCHOW_change_bool == TRUE),
                          clust_cols = all_FC_cols$Ins[grep("CHOW", all_FC_cols$Ins)],
                          tile_border_size = 0,
                          aspect_ratio_fixed = FALSE,
                          scale_colours_manually = TRUE,
                          mid_colour_threshold = 1.5,
                          comparisons = c("Ins"),
                          CHOW_only = TRUE)
ggsave_pdfpng(file = "output/images/analysis/insulin_regulation/insreg_changes/CHOW_Strain_aov/hmap_CHOWStrain_aov_straindiff",
              width = 2.5, height = 4)
```

HFD/CHOW inbas heatmaps
```{r}
for (strain in all_levels$Strain){
  insbas_cols <- map(c("CHOW", "HFD"),
                     ~paste(strain, ., "bas_vs", strain, ., "ins_logFC", sep = "_"))
  insbas_diet_FC <- paste(strain, "_CHOW_insbas_vs_", strain, "_HFD_insbas_logFC", sep = "")
  phos_data_proc_insreg[, insbas_diet_FC] <- phos_data_proc_insreg[, insbas_cols[[2]]] - 
    phos_data_proc_insreg[, insbas_cols[[1]]]
  data_wNAs_filt[, insbas_diet_FC] <- data_wNAs_filt[, insbas_cols[[2]]] - 
    data_wNAs_filt[, insbas_cols[[1]]]
}
##Heatmap function
insresp_dietresp_cols <- colnames(phos_data_proc_insreg)[grep("_insbas_", colnames(phos_data_proc_insreg))]
heatmap_GxEphos_clustered_insbasdietresp <- function(data,
                                                     ...){
  #Cluster for ordering
  dist_m <- dist(data[, insresp_dietresp_cols])
  hclust <- hclust(dist_m)
  data <- data[hclust$order, ]
  data$order_col <- 1:nrow(data)
  #Hmap
  output_plot <- fc_sig_heatmap(data,
               fc_cols_wo_pvals = insresp_dietresp_cols,
               x_axis_names = all_levels$Strain,
               order_column = "order_col",
               ...)
  return(output_plot)
}

##Heatmaps
#All sites with Diet or StrainxDiet effect
DSxD_overall <- rownames(subset(phos_data_proc_insreg,
                                 insregdiff_Dietoverall_change_bool == TRUE),)
heatmap_GxEphos_clustered_insbasdietresp(phos_data_proc_insreg[DSxD_overall, ],
                          tile_border_size = 0,
                          aspect_ratio_fixed = FALSE,
                          scale_colours_manually = TRUE,
                          mid_colour_threshold = 1.25,
                          legend_title = "log2 insresp HFD/CHOW")
ggsave_pdfpng("output/images/analysis/insulin_regulation/insreg_changes/Diet_2wayaov/hmap_DSxDaov_Dietoveralldiff_HFDonCHOW",
              width = 4, height = 4)
```

Volcano plot
```{r}
##Volcano plot of all insreg
volcano_plot_coloured(data = phos_data_proc_insreg,
                          pval_col = "ins3wayaovint_q",
                          FC_col = "ins_bas_logFC_StrainDietmax",
                          colour_col = "insreg_dir",
                          colour_col_levels = c("unregulated", "up", "down"),
                          colour_col_colours = c(ins_updown_colours, 
                                                "unregulated" = "black")) +
      labs(x = "Max Strain-Diet log2(ins/bas)", y = "-log10 q-value")
ggsave_pdfpng("output/images/analysis/insulin_regulation/global_vis/vplot_insregupdown", width = 3, height = 3)
```



####Characterising insulin regulation
###PhosphositePlus insulin upstream annotations
I see how many insulin-regulated phosphopeptides have insulin as an upstream treatment in PSP
```{r}
##Set up data
PSP_insulin <- read_delim("data/intermediate/biol_databases/PSP/PSP_insulin_treatment_20221002.txt")
insreg_data <- subset(phos_data_proc_insreg, insreg_bool == TRUE) %>%
  annotation_search_mapback(annotation_groups = c("PSP"))
##Make PSP insulin treatment into phos data
insreg_data$PSP_insulin <- FALSE
insreg_data[which(insreg_data$PSP_SITE_GRP_ID %in% PSP_insulin$SITE_GRP_ID), "PSP_insulin"] <- TRUE
table(insreg_data$PSP_insulin)
##Make and visualise summary
insreg_PSP_insulin_sum <- summariser_twoway(insreg_data, "insreg_dir", "PSP_insulin") %>%
  subset(insreg_dir %in% c("up", "down") &
           PSP_insulin %in% c(FALSE, TRUE)) %>%
  mutate(PSP_insulin = factor(PSP_insulin, levels = c(TRUE, FALSE)))
  
#Up and down
ggplot(insreg_PSP_insulin_sum, 
       aes(x = PSP_insulin, y = Freq, fill = insreg_dir)) +
  geom_col(position = "stack", width = 0.8) + 
  comfy_theme(include_xaxis = FALSE, rotate_x_text = TRUE) +
  scale_fill_manual(values = ins_updown_colours,
                    name = "Insulin regulation",
                    labels = c("Upregulated", "Downregulated")) +
  theme(axis.line.x = element_blank()) +
  labs(y = "Phosphopeptides")
ggsave_pdfpng("output/images/analysis/insulin_regulation/insreg/characterisation/bplot_PSPinsulin_insreg_updown",
              width = 1.9, height = 1.5)
#No up or down
ggplot(insreg_PSP_insulin_sum, 
       aes(x = PSP_insulin, y = Freq)) +
  geom_col(position = "stack", width = 0.8, fill = "#000000") + 
  comfy_theme(include_xaxis = FALSE, rotate_x_text = TRUE) +
  theme(axis.line.x = element_blank()) +
  labs(y = "Phosphopeptides")
ggsave_pdfpng("output/images/analysis/insulin_regulation/insreg/characterisation/bplot_PSPinsulin_insreg",
              width = 0.8, height = 1.5)
```

###Comparison to other insulin signalling ppomes
Needham 2022 Nat Biotech
```{r}
###Functions
unique_notNA <- function(x){
  x <- x[which(!is.na(x))]
  if (length(x) == 0){
    return(NA)
  } else {
   x <- unique(x)
   return(x) 
  }
}

###Load in and process data
needham_rawest <- read_csv("data/intermediate/biol_databases/supplementary_tables/Needham_NatBiotech_2022/Needham_2022_ppome.csv")
needham_raw <- needham_rawest %>%
  dplyr::rename("standard_name" = "gene_uniprot_site_multiplicity") %>%
  mutate(uniprot = strsplit(standard_name, "_") %>% map(~.[2]) %>% unlist) %>%
  mutate(uniprot_site = paste(uniprot, Site, sep = "_")) %>%
  as.data.frame
##Remove duplicate rows and assign rownames
which(table(needham_raw$standard_name) > 1)
duplicate_names <- c("MYH8_P13535_S1040_1",
                     "MYH8_P13535_S1513_1",
                     "TPM3_P06753_S207_1",
                     "TPM3_P06753_S216_1")
for (name in duplicate_names){
  indices <- which(needham_raw$standard_name == name)
  needham_raw <- needham_raw[-indices[1], ]
}
rownames(needham_raw) <- needham_raw$standard_name
##Assign insreg with dir
needham_raw$insreg_dir <- "unregulated"
needham_raw[which(needham_raw$sig_RestIns_RestBas == "+" &
                    needham_raw$logfc_RestIns_RestBas > 0), "insreg_dir"] <- "up"
needham_raw[which(needham_raw$sig_RestIns_RestBas == "+" &
                    needham_raw$logfc_RestIns_RestBas < 0), "insreg_dir"] <- "down"
table(needham_raw$insreg_dir)
##Add PSP SITE_GRP_IDs
#Load in PSP
psp_directory <- "data/intermediate/biol_databases/PSP/20220808/"
source(paste(home_directory, "scripts/PSP_JvG.R", sep = ""))
psp_data <- load_psp_data(filename = "Phosphorylation_site_dataset_20220808",
                          directory = psp_directory)
needham_SGIDs <- uniprotsite_to_sitegroupid(uniprot_sites = needham_raw$uniprot_site,
                                            psp_phos_data = psp_data,
                                       restrict_to_phos = TRUE)
needham_raw$PSP_SITE_GRP_ID <- unlist(needham_SGIDs)


###Map into my data
phos_data_wneedham <- phos_data_proc_insreg %>%
  annotation_search_mapback(., annotation_groups = "PSP") %>%
  .[, c("gene", "uniprot", "site", "multiplicity",
        "uniprot_site", "standard_name", "PSP_SITE_GRP_ID",
        "insreg_bool", "insreg_dir")]
common_SGIDs <- intersect(needham_raw$PSP_SITE_GRP_ID,
                          phos_data_wneedham$PSP_SITE_GRP_ID)

###Lists of regulated sites
insreg_SGIDs_list <- map(list("up" = c("up"),
                              "down" = c("down"),
                              "either" = c("up", "down")), function(x){
                                lst <- map(list("GxE" = phos_data_wneedham,
                                             "needham" = needham_raw), function(data){
                                               data <- data[which(data$insreg_dir %in% x), ]
                                               return(unique_notNA(data$PSP_SITE_GRP_ID))
                                             })
                              })
insreg_SGIDs_list_common <- map(insreg_SGIDs_list, function(lst){
  map(lst, ~intersect(., common_SGIDs))
})


###Test overrepresentation
insreg_overrep <- map(insreg_SGIDs_list_common, function(lst){
  test <- fishers_DE_pathway(background_genes = common_SGIDs,
                             DE_genes = lst$GxE,
                             pathway_genes = lst$needham,
                             alternative = "greater")
  return(test)
})

###Visualise overlap
##venn diagrams
venn_dir <- "output/images/analysis/insulin_regulation/characterisation/vs_Needham2022/venn_common_insreg_"
venn_width <- 3
venn_height <- 3
#either
ggVennDiagram_nice(list = insreg_SGIDs_list_common$either,
                   colours = brewer.pal(9, "Greys")[1:6],
                   fill_limits = c(0, NA))
ggsave_pdfpng(file = paste(venn_dir, "_either", sep = ""), width = venn_width, height = venn_height)
```

###Pathway enrichment
Set up
```{r}
insreg_genes <- subset(phos_data_proc_insreg, insreg_bool == TRUE) %>% .$gene %>% unique
bkd_genes <- unique(phos_data_proc_insreg$gene)
```

GO BPs
```{r}
###Run enrichment
insreg_GOBP_enr <- GO_enricher(background_genes = bkd_genes,
                                DE_genes = insreg_genes,
                                gene_label = "SYMBOL",
                                organism_database = org.Mm.eg.db,
                                ontology = "BP",
                                pathway_DE_intersection_threshold = 3)
###Visualise
enrichment_barplot_pval(data = insreg_GOBP_enr,
                        pval_col = "adj_pval",
                        colour_col = "ES_log2",
                        colours = brewer.pal(9, "Greys"),
                        limits_from0 = TRUE)
ggsave_pdfpng(file = "output/images/analysis/insulin_regulation/characterisation/enrichment/bplot_insreg_GO_BP",
              width = 6, height = 4)
```


###Output
```{r}
save(data_wNAs_filt,
     file = "output/data/data_wNAs_filt__2.RData")
save(phos_data_proc_insreg,
     file = "output/data/phos_data_proc_insreg__4.RData")
```



















