###Background
Here I characterise Strain differences in insulin regulation as identified in 03_insulin_regulation.Rmd

###Initialise
```{r}
library(tidyverse)
library(purrr)
library(ggplot2)
library(qvalue)
home_directory <- "..\\"
source(paste(home_directory, "scripts/essential_visualisations_JvG.R", sep = ""))
source(paste(home_directory, "scripts/enrichment_analysis_JvG.R", sep = ""))
source("..\\scripts/01_objects__1.R")
source("..\\scripts/02_global_functions__1.R")
source("scripts/03_basic_functions.R")
source("scripts/09_insregdiff.R")

load("data/intermediate/phos_data/phos_data_proc_insreg__4.RData")
```

###Set up data 
```{r}
##Make insreg data
insreg_data <- subset(phos_data_proc_insreg, insreg_bool == TRUE)
```

###Canonical insulin signalling
Here I look at canonical insulin signalling proteins and phosphosites

Set up
```{r}
##Directory
canins_dir <- "output/images/analysis/insulin_regulation/insreg_changes/CHOW_Strain_aov/caninssig/"
```

##Canonical insulin signalling proteins
This is a list of "canonical insulin signalling proteins" compiled from several ontologies, which features in 2022 Nat Biotech paper (doi.org/10.1038/s41587-021-01099-9 )
```{r}
###Set up
##Load in and process
can_ins_sig_proteins_EN <- readRDS("data/intermediate/biol_databases/can_ins_sig/can_ins_prots.rds") %>%
  tolower %>% 
  strsplit("") %>% map(~paste(c(toupper(.[1]), .[-1]), collapse = "")) %>% unlist

##Combine with insreg_data
insreg_data_caninsEN <- insreg_data
insreg_data_caninsEN$caninssig_EN <- FALSE
insreg_data_caninsEN[which(insreg_data_caninsEN$gene %in% can_ins_sig_proteins_EN), "caninssig_EN"] <- TRUE


##Strain changes
Straindiff_caninsEN_summary <- summary_StrainCHOW_change(insreg_data_caninsEN,
                                                    Var2 = "caninssig_EN")
#y axis is proportion with strain effect
ggplot(subset(Straindiff_caninsEN_summary$bool, 
              insregdiff_StrainCHOW_change_bool == TRUE), 
       aes(x = caninssig_EN, y = prop_of_caninssig_EN*100)) +
  geom_col(fill = "black", width = 0.8) +
  comfy_theme() +
  labs(y = "% Strain effect",
       x = "Canonical insulin signalling protein")
ggsave_pdfpng(paste(canins_dir, "bplot_Straindiffbool_caninsEN_prop_ystrain",
                    sep = ""),
              width = 1.25, height = 1.5)

#Fisher's exact
fishers_DE_pathway(background_genes = rownames(insreg_data_caninsEN),
                   DE_genes = subset(insreg_data_caninsEN, 
                                     caninssig_EN == TRUE) %>% rownames,
                   pathway_genes = subset(insreg_data_caninsEN, 
                                          insregdiff_StrainCHOW_change_bool == TRUE) %>% rownames,
                   alternative = "two.sided")
```





























