###Background
Here I perform kinase analysis

###Initialise
```{r}
library(tidyverse)
library(purrr)
home_directory <- "..\\"
source(paste(home_directory, "scripts/essential_visualisations_JvG.R", sep = ""))
source(paste(home_directory, "scripts/boxplots_JvG.R", sep = ""))
source(paste(home_directory, "scripts/enrichment_analysis_JvG.R", sep = ""))
source("..\\scripts/01_objects__1.R")
source("..\\scripts/02_global_functions__1.R")
source("scripts/02_basic_visualisations.R")
source("scripts/03_basic_functions.R")
source("scripts/06_annotation.R")
source("scripts/11_enrichment.R")

load("data/intermediate/phos_data/annotation/phos_data_annotation__1.RData")
load("data/intermediate/phos_data/phos_data_proc_insreg__4.RData")
load("data/intermediate/phos_data/data_wNAs_filt__2.RData")
#Add PSP_SITE_GRP_IDs
phos_data_proc_insreg <- annotation_search_mapback(phos_data_proc_insreg,
                                                   annotation_groups = "PSP")
data_wNAs_filt <- annotation_search_mapback(data_wNAs_filt,
                                                   annotation_groups = "PSP")

#Load in kinase substrate data
load("data/intermediate/biol_databases/psp_kin_sub_list_invivo_noauto_Gsk3i__1.RData")

#Canonical kinases
can_kins <- c("Akt",
              "mTOR",
              "p70S6K",
              "p90RSK",
              "GSK3")

#KSEA colours
KSEA_colours <- map(fivestraincols_main, ~rep(., 2)) %>% unlist
```





####Run stats 
I perform KSEA in each insulin-stimulated mouse using the insulin response

```{r}
##Set up args
trial_n <- 1000
#Get columns ready
basnorm_cols <- colnames(phos_data_proc_insreg) %>%
  .[grep("basnorm_\\d+$", .)]
#KSEA args
KSEA_insbas_args <- list(
  "ins_resp" = list(
    
    "num_cols" = basnorm_cols,
    "conditions" = strsplit(basnorm_cols, "_") %>% 
      map(~paste(.[c(1, 2, 5)], collapse = "_")) %>% unlist,
    "kin_sub_list" = psp_kin_sub_list_invivo_noauto_Gsk3i
  )
)
##Set up substrate data by performing filtering
#insresp quantified in each straindiet
insresp_cols <- colnames(phos_data_proc_insreg) %>% .[grep("_basnorm_\\d+$", .)]
insresp_StrainDiet_quants <- map(all_levels$StrainDiet,
                                 function(strain_diet){
                                   suffix <- paste(strain_diet, "_ins_basnorm_\\d+$", sep = "")
                                   num_data <- phos_data_proc_insreg %>% .[, grep(suffix, colnames(.))]
                                   quants <- rowSums(!is.na(num_data), na.rm = TRUE)
                                 }) %>% 
  purrr::reduce(cbind)
insresp_StrainDiet_allquant_bool <- rowSums(insresp_StrainDiet_quants > 0) == 10
#Filter: quantified in >= 1/2 samples, and at least one insresp value in each StrainDiet combination
phos_data_proc_insreg_forKSEA <- phos_data_proc_insreg[insresp_StrainDiet_allquant_bool, ]
phos_data_proc_insreg_forKSEA <- subset(phos_data_proc_insreg_forKSEA,
                                           num_quant_samples >= 47)

##Run KSEA
set.seed(57)
KSEA_insbas <- map(KSEA_insbas_args,
                          function(x){
                            phos_data_proc_insreg
                            #Set up data
                            data <- phos_data_proc_insreg_forKSEA
                            num_data <- data[, x$num_cols]
                            #Run KSEA
                          KSEA_output <- 
                          KSEA_from_list_multconds(num_data = num_data,
                                                  conditions = x$conditions, 
                                                  stat_names = data$PSP_SITE_GRP_ID,
                                                  kin_sub_list = x$kin_sub_list,
                                                  trial_n = trial_n,
                                                  merge = TRUE,
                                                  promisc_threshold = 4)
                          return(KSEA_output)
                          })

##Calculate signed -log10pvals
#If p = 0, set -log10 p to 4 (this is equivalent to p = 0.0001, which is impossible to get with n = 1000 trials)
KSEA_insbas <- map(KSEA_insbas,
                   function(data){
                     #Get conditions
                     conditions <- colnames(data) %>%
                       .[grep("_ES$", .)] %>%
                       gsub("_ES$", "", .)
                     #Loop over conditons
                     for (condition in conditions){
                       colname <- paste(condition, "_signlogp", sep = "")
                       nlogps <- signed_nlog10_pval(FCs = as.numeric(data[, paste(condition, "_ES", 
                                                                                  sep = "")]),
                                                    pvals = as.numeric(data[, paste(condition, "_p", 
                                                                                    sep = "")]),
                                                    inf_val = 4)
                       data[, colname] <- nlogps
                     }
                     return(data)
                   })

##Sum number of significantly regulated samples/conditions
KSEA_insbas <- map(KSEA_insbas,
                   function(data){
                     sig_m <- data[, grep("_p$", colnames(data))] < 0.05
                     data$num_sig_samples <- rowSums(sig_m, na.rm = TRUE)
                     return(data)
                   })

##Subset for kinases significantly regulated in >= 5 samples or >= 1 strain-diet condition
KSEA_insbas_sigkins <- KSEA_insbas
KSEA_insbas_sigkins$ins_resp <- subset(KSEA_insbas_sigkins$ins_resp,
                                         num_sig_samples >= 5)
```



####Canonical kinases
Visualise
```{r}
KSEA_insbas_bplotter(KSEA_list = KSEA_insbas,
                     kinases = can_kins,
                     dir = "output/images/analysis/kinases/insbas_KSEA/bplot_KSEA_cankins_",
                     width = 4, height = 2.5)
```


####Significantly regulated kinases
These are kinases significantly regulated in >= 5 samples

###Strain and diet differences in significant kinases
Here I perform tests to identify kinases that differ in insulin regulation across strains and diets

##Run stats
Set up
```{r}
sig_threshold <- 0.05
KSEA_insbas_sigkins_long <- KSEA_pivot_longer(KSEA_insbas_sigkins$ins_resp)
source("scripts/08_ins_reg.R")
```

CHOW anova for Strain effects
```{r}
##Run ANOVAs
KSEA_CHOW_aov_ps <- map(levels(KSEA_insbas_sigkins_long$kinase),
                              function(kin){
                               temp_test <- aov(val ~ Strain, 
                                                 subset(KSEA_insbas_sigkins_long, 
                                                        kinase == kin &
                                                          Diet == "CHOW")) 
                               pval <- summary(temp_test)[[1]][1, 5]
                               return(pval)
                              }) %>% unlist
names(KSEA_CHOW_aov_ps) <- levels(KSEA_insbas_sigkins_long$kinase)
#Adjust pvalues
KSEA_CHOW_aov_adjps <- p.adjust(KSEA_CHOW_aov_ps, method = "fdr")
KSEA_CHOW_aov_sigkins <- names(KSEA_CHOW_aov_adjps)[which(KSEA_CHOW_aov_adjps < sig_threshold)]
#Combine
KSEA_CHOW_aov_results <- data.frame("CHOWStrain_aov_p" = KSEA_CHOW_aov_ps,
                                    "CHOWStrain_aov_p_adj" = KSEA_CHOW_aov_adjps)
```

Two-way anova for StrainxDiet and Diet effects
Perform anovas
```{r}
##Run ANOVAs
KSEA_twowayaov_ps <- map(levels(KSEA_insbas_sigkins_long$kinase),
                              function(kin){
                               temp_test <- aov(val ~ Strain*Diet, 
                                                 subset(KSEA_insbas_sigkins_long, 
                                                        kinase == kin)) 
                               pvals <- summary(temp_test)[[1]][2:3, 5]
                               names(pvals) <- c("Diet", "StrainxDiet")
                               return(pvals)
                              }) %>%
  purrr::reduce(rbind) %>% as.data.frame
rownames(KSEA_twowayaov_ps) <- levels(KSEA_insbas_sigkins_long$kinase)

#Adjust pvalues
KSEA_twowayaov_adjps <- KSEA_twowayaov_ps
for (col in colnames(KSEA_twowayaov_adjps)){
  KSEA_twowayaov_adjps[, col] <- p.adjust(KSEA_twowayaov_adjps[, col],
                                          method = "fdr")
}
KSEA_twowayaov_SxD_sigkins <- subset(KSEA_twowayaov_adjps, StrainxDiet < sig_threshold) %>%
  rownames

#Add ANOVA pvalues
KSEA_twowayaov_results <- data.frame("SxD_aov_Diet_p" = KSEA_twowayaov_ps$Diet,
                                    "SxD_aov_StrainxDiet_p" = KSEA_twowayaov_ps$StrainxDiet,
                                    "SxD_aov_Diet_p_adj" = KSEA_twowayaov_adjps$Diet,
                                    "SxD_aov_StrainxDiet_p_adj" = KSEA_twowayaov_adjps$StrainxDiet)
rownames(KSEA_twowayaov_results) <- rownames(KSEA_twowayaov_ps)
#Add sig classes
KSEA_twowayaov_results$SxD_aov_sigclass <- NA
KSEA_twowayaov_results[which(KSEA_twowayaov_results$SxD_aov_Diet_p_adj < sig_threshold), 
                      "SxD_aov_sigclass"] <- "Diet"
KSEA_twowayaov_results[which(KSEA_twowayaov_results$SxD_aov_StrainxDiet_p_adj < sig_threshold), 
                      "SxD_aov_sigclass"] <- "StrainxDiet"
```


##Explore significant kinases
Export for summary
```{r}
#Set up
KSEA_twowayaov_sig_df <- cbind(KSEA_CHOW_aov_results,
                               KSEA_twowayaov_results) %>%
  subset(CHOWStrain_aov_p_adj < sig_threshold |
           !is.na(SxD_aov_sigclass))
```

Visualise
```{r}
##Subset for significant kinases
KSEA_insbas_twowayaov_sigkins <- list(
  "CHOWStrain" = subset(KSEA_CHOW_aov_results, 
                        CHOWStrain_aov_p_adj < sig_threshold) %>% rownames,
  "StrainxDiet" = subset(KSEA_twowayaov_results, 
                         SxD_aov_sigclass == "StrainxDiet") %>% rownames,
  "Diet" = subset(KSEA_twowayaov_results, 
                         SxD_aov_sigclass == "Diet") %>% rownames
)
KSEA_insbas_twowayaov_sigkins$SxD_or_Diet <- 
  unique(c(KSEA_insbas_twowayaov_sigkins$StrainxDiet,
           KSEA_insbas_twowayaov_sigkins$Diet))
KSEA_insbas_twowayaov_sigkins$all <- unique(unlist(KSEA_insbas_twowayaov_sigkins))

KSEA_insbas_twowayaov_sigkins_list <- map(KSEA_insbas_twowayaov_sigkins, 
                                          function(rows){map(KSEA_insbas_sigkins, 
                                                             ~.[rows, ])})

##Heatmaps
KSEA_insbas_hmapper(KSEA_insbas_twowayaov_sigkins_list$CHOWStrain,
                    conditions = all_levels$StrainDiet %>% .[grep("CHOW", .)],
                    dir = paste("output/images/analysis/kinases/insbas_KSEA/hmap_KSEA_",
                                "StrainCHOW", 
                                "_sig", sep = ""),
                    width = 2.75, height = 4)
KSEA_insbas_hmapper(KSEA_insbas_twowayaov_sigkins_list$SxD_or_Diet,
                    conditions = all_levels$StrainDiet,
                    dir = paste("output/images/analysis/kinases/insbas_KSEA/hmap_KSEA_",
                                "SxD_or_Diet", 
                                "_sig", sep = ""),
                    width = 4, height = 4)
KSEA_insbas_hmapper(KSEA_insbas_twowayaov_sigkins_list$all,
                    conditions = all_levels$StrainDiet,
                    dir = paste("output/images/analysis/kinases/insbas_KSEA/hmap_KSEA_",
                                "all", 
                                "_sig", sep = ""),
                    width = 4, height = 4)
```


###Correlation with glucose uptake
```{r}
###Set up
#Load in pheno data
load("data/intermediate/pheno_data/pheno_data__5.RData")
pheno_col <- "sol_p2DG_weightnorm_rate"
#Set up KSEA data
KSEA_data_tocorr <-KSEA_insbas_sigkins$ins_resp
KSEA_data_tocorr <- KSEA_data_tocorr %>%
  .[, grep("_ES$", colnames(.))]
colnames(KSEA_data_tocorr) <- strsplit(colnames(KSEA_data_tocorr), "_") %>%
  map(~paste(c(.[1], .[2], "ins", .[3]), collapse = "_")) %>% unlist
#Combine with GU data
KSEA_GU_data <- combine_phos_pheno_data(phos_data = KSEA_data_tocorr,
                        pheno_data = pheno_data,
                        pheno_cols = pheno_col,
                        phos_num_cols = colnames(KSEA_data_tocorr),
                        phos_UIDs = colnames(KSEA_data_tocorr),
                        phos_rows = rownames(KSEA_data_tocorr))
#Summarise over strains and diets
num_cols <- c(rownames(KSEA_data_tocorr), pheno_col)
KSEA_GU_data_sum <- map(levels(KSEA_GU_data$StrainDiet),
                        function(strain_diet){
                          data <- subset(KSEA_GU_data, StrainDiet == strain_diet) %>% .[, num_cols]
                          data_sum <- apply(data, 2, FUN = "median", na.rm = TRUE)
                          return(data_sum)
                        }) %>%
  purrr::reduce(rbind) %>% as.data.frame
rownames(KSEA_GU_data_sum) <- levels(KSEA_GU_data$StrainDiet)
KSEA_GU_data_sum$StrainDiet <- rownames(KSEA_GU_data_sum)
KSEA_GU_data_sum[, c("Strain", "Diet")] <- strsplit(KSEA_GU_data_sum$StrainDiet, "_") %>%
  purrr::reduce(rbind)
KSEA_GU_data_sum <- mutate(KSEA_GU_data_sum,
                           StrainDiet = factor(StrainDiet, levels = all_levels$StrainDiet),
                           Strain = factor(Strain, levels = all_levels$Strain),
                           Diet = factor(Diet, levels = all_levels$Diet))

###Run correlation tests
source("scripts/10_GU_correlations.R")
#Corr tests
KSEA_corr_data <- list("all_data" = KSEA_GU_data, 
                          "sum_data" = KSEA_GU_data_sum)
KSEA_GU_corrs <- map(KSEA_corr_data,
                     ~phos_GU_correlator_mult_fromcomb(phos_GU_data = .,
                                 ppeptides = rownames(KSEA_insbas_sigkins$ins_resp),
                                 cor_method = "pearson"))
```

















