###Background
Here I perform network correlation analysis to identify co-regulated clusters of insulin-regualted ppeptides

###Initialise
```{r}
library(tidyverse)
library(purrr)
home_directory <- "..\\"
source(paste(home_directory, "scripts/PSP_JvG.R", sep = ""))
psp_directory <- paste(home_directory,
                      "data/biol_databases/phosphosite_plus/20220808/",
                      sep = "")

source(paste(home_directory, "scripts/essential_visualisations_JvG.R", sep = ""))
source(paste(home_directory, "scripts/enrichment_analysis_JvG.R", sep = ""))
source(paste(home_directory, "scripts/stats_JvG.R", sep = ""))
source("..\\scripts/01_objects__1.R")
source("..\\scripts/02_global_functions__1.R")
source("scripts/01_QC.R")
source("scripts/02_basic_visualisations.R")
source("scripts/03_basic_functions.R")
source("scripts/06_annotation.R")
source("scripts/11_enrichment.R")
source("scripts/12_correlation_network_analysis.R")

load("data/intermediate/phos_data/annotation/phos_data_annotation__1.RData")
load("data/intermediate/phos_data/phos_data_proc_insreg__4.RData")
load("data/intermediate/phos_data/data_wNAs_filt__2.RData")
#Add PSP_SITE_GRP_IDs
phos_data_proc_insreg <- annotation_search_mapback(phos_data_proc_insreg,
                                                   annotation_groups = "PSP")
data_wNAs_filt <- annotation_search_mapback(data_wNAs_filt,
                                                   annotation_groups = "PSP")

#Load in kinase substrate data
load("data/intermediate/biol_databases/psp_kin_sub_list_invivo_noauto_Gsk3i__1.RData")

#Basnorm cols
basnorm_cols <- colnames(data_wNAs_filt) %>% 
                             .[grep("_basnorm_\\d+$", .)]
phos_num_cols <- UIDs[which(UIDs %in% colnames(phos_data_proc_insreg))]

#Clsuter colours
cluster_colours <- c("1" = "#7f4393",
                     "2" = "#ac5781",
                     "3" = "#ba984d",
                     "4" = "#e4e029",
                     "5" = "#b2cc37",
                     "6" = "#82ac85",
                     "7" = "#c4d7ef",
                     "8" = "#287240")
```


####WGCNA

###Run WGCNA
```{r}
##Set up
data_preWGCNA <- t(subset(data_wNAs_filt, insreg_bool == TRUE) %>% .[, basnorm_cols])

##Get soft threshold
#Power = 3 gives a high fit but then it drops massively
indices <- 1:30
soft_thresh <- pickSoftThreshold(data_preWGCNA, verbose = 5,
                                 powerVector = indices)
plot(soft_thresh$fitIndices[, 1],
     -sign(soft_thresh$fitIndices[, 3])*soft_thresh$fitIndices[, 2])

##Run WGCNA
WGCNA_net <- blockwiseModules(data_preWGCNA, power = 3,
                        TOMtype = "unsigned", 
                        minModuleSize = 15, deepSplit = 3,
                        reassignThreshold = 0, mergeCutHeight = 0.25,
                        numericLabels = TRUE, pamRespectsDendro = FALSE,
                        verbose = 3)

#Extract clusters
clust_names <- sort(unique(WGCNA_net$colors))
WGCNA_clusters <- map(clust_names,
                      ~names(WGCNA_net$colors)[which(WGCNA_net$colors == .)])
names(WGCNA_clusters) <- as.character(clust_names)
WGCNA_clusters <- WGCNA_clusters[which(names(WGCNA_clusters) != "0")]
WGCNA_clusters_genes <- map(WGCNA_clusters, function(x){
  x_split <- strsplit(x, "_")
  x_genes <- map(x_split, ~.[1]) %>% unlist %>% unique
  return(x_genes)
})

##Inspect WGCNA output
table(WGCNA_net$colors)
mergedColors <- labels2colors(WGCNA_net$colors)
plotDendroAndColors(WGCNA_net$dendrograms[[1]],
                    mergedColors[WGCNA_net$blockGenes[[1]]],
                    "Module colours",
                    dendroLabels = FALSE, hang = 0.03,
                    addGuide = TRUE, guideHand = 0.05)
```

###Visualise
Basic heatmap
```{r}
###Set up
##Correaltion natrix
WGCNA_cor_m <- cor(data_preWGCNA, use = "pairwise.complete.obs")
##Correlation colour scale
#Function to allow adjustment of colour gradient
corr_scale <- function(mid_threshold = 0.5){
  #Make positive numbers
  pos_nums <- c(seq(from = 0, to = mid_threshold, length.out = 3),
                seq(from = mid_threshold, to = 1, length.out = 3)[-1])
  neg_nums <- -(pos_nums)
  all_nums <- sort(unique(c(neg_nums, pos_nums)))
  return(all_nums)
}
hmap_cols <- colorRamp2(breaks = corr_scale(0.5),
                        colors = rev(brewer.pal(9, "RdBu")))
##Annotation for cluster
cluster_cols <- c("#989898",
                  cluster_colours)
names(cluster_cols) <- unique(WGCNA_net$colors)
clust_lab <- HeatmapAnnotation(cluster = WGCNA_net$colors,
                               col = list(cluster = cluster_cols))
##Ordered data by hclust within WGCNA
data_preWGCNA_ordered <- hclust_within_WGCNAclust(data_preWGCNA,
                                                  WGCNA_net)

##hclsut within WGCNA clusters
pdf(paste("output/images/analysis/corr_network/WGCNA/",
          "corhmap_insreg_WGCNA_smallerclust",
          ".pdf",
          sep = ""),
    width = 7, height = 6)
Heatmap(WGCNA_cor_m, col = hmap_cols,
        show_row_names = F, show_column_names = F,
        row_order = colnames(data_preWGCNA_ordered), column_order = colnames(data_preWGCNA_ordered),
        top_annotation = clust_lab)
dev.off()
```



####Characterise clusters

###GO enrichment
Perform enrichment across all clusters
```{r}
##Set up
pathway_DE_intersection_threshold <- 3

##Get GO pathways lists
relevant_GOIDs <- map(c("BP" = "BP", "CC" = "CC"), function(ont){
  ##Get all pathways that intersect sufficiently with at least one cluster
  relevant_GOIDs_list <- relevant_GOIDS(DE_genes = unique(unlist(WGCNA_clusters_genes)),
                                        gene_label = "SYMBOL",
                                        organism_database = org.Mm.eg.db,
                                        ontology = ont)
  #Keep only those that intersect sufficiently with at least one cluster
  GOIDs_int_bool_list <- map(WGCNA_clusters_genes, function(clust){
    map(relevant_GOIDs_list, 
      ~length(intersect(., clust)) >= pathway_DE_intersection_threshold) %>% 
    unlist
  })
  GOIDs_int_bool_sum <- purrr::reduce(GOIDs_int_bool_list, cbind) %>%
    rowSums
  relevant_GOIDs_list_filt <- relevant_GOIDs_list[which(GOIDs_int_bool_sum > 0)]
  #Rename using GO term
  GO_terms <- AnnotationDbi::select(GO.db,
                                   names(relevant_GOIDs_list_filt),
                                   columns = "TERM",
                                   keytype = "GOID")$TERM
  names(relevant_GOIDs_list_filt) <- GO_terms
     return(relevant_GOIDs_list_filt)
})

##Run enrichment
#Background: Entire ppome
cluster_overrep_GO_bkgppome_compr_df <- map(relevant_GOIDs, function(GOIDs){
  clust_enricher(clust_genes = WGCNA_clusters_genes,
                 bkd_genes = unique(phos_data_proc_insreg$gene),
                 pways_list = GOIDs)
})
```

Visualisation

Heatmaps of enrichment
```{r}
GO_dir <- "output/images/analysis/corr_network/WGCNA/GO/hmap_WGCNA_GO_"
##Bkd: ppome
#Same colour scale
overrep_hmap(data = cluster_overrep_GO_bkgppome_compr_df$BP,
             scale_colours_manually = TRUE,
             mid_colour_threshold = 3,
             high_colour_threshold = 6.7)
ggsave_pdfpng(paste(GO_dir, "BP_samescale", sep = ""),
              width = 5.5, height = 2.5)
overrep_hmap(data = cluster_overrep_GO_bkgppome_compr_df$CC,
             scale_colours_manually = TRUE,
             mid_colour_threshold = 3,
             high_colour_threshold= 6.7)
ggsave_pdfpng(paste(GO_dir, "CC_samescale", sep = ""),
              width = 4, height = 2)
#Diff colour scale
overrep_hmap(data = cluster_overrep_GO_bkgppome_compr_df$BP,
             scale_colours_manually = TRUE,
             mid_colour_threshold = 4)
ggsave_pdfpng(paste(GO_dir, "BP", sep = ""),
              width = 5.5, height = 2.5)
overrep_hmap(data = cluster_overrep_GO_bkgppome_compr_df$CC,
             scale_colours_manually = TRUE,
             mid_colour_threshold = 2)
ggsave_pdfpng(paste(GO_dir, "CC", sep = ""),
              width = 4, height = 2)
```


###Kinase enrichment



Perform enrichment
```{r}
##Set up
load("data/intermediate/biol_databases/psp_kin_sub_list_invivo_noauto_Gsk3i__1.RData")
##Get WGCNA cluster SITE_GRP_IDs
WGCNA_clusters_SGIDs <- map(WGCNA_clusters, function(clust){
  SITE_GRP_IDs <- phos_data_annotation[clust, "PSP_SITE_GRP_ID"] %>%
    .[which(!is.na(.))] %>% unique
})

##Restrict to kinases with sufficient overlap
##Set up
pathway_DE_intersection_threshold <- 3

psp_kin_sub_int_bool_list <- map(WGCNA_clusters_SGIDs, function(clust){
  map(psp_kin_sub_list_invivo_noauto_Gsk3i,
      ~length(intersect(., clust)) >= pathway_DE_intersection_threshold) %>% unlist
})
psp_kin_sub_int_bool_sum <- purrr::reduce(psp_kin_sub_int_bool_list, cbind) %>%
  rowSums
psp_kin_sub_list_relevant <- psp_kin_sub_list_invivo_noauto_Gsk3i[which(psp_kin_sub_int_bool_sum > 0)]

##Remove promiscuous psites
#Get promiscuos SGIDS. promisc_threshold = 4 was used for KSEA
SGIDs <- unique(unlist(WGCNA_clusters_SGIDs))
promisc_bool <- promisc_psites_trim(stat_names = SGIDs,
                                    kin_sub_list = psp_kin_sub_list_relevant,
                                    promisc_threshold = 4)
promisc_SGIDs <- SGIDs[!promisc_bool]
#Remove from kinase sub list
psp_kin_sub_list_relevant_trim <- map(psp_kin_sub_list_relevant, function(subs){
  subs <- subs[which(subs %in% promisc_SGIDs == FALSE)]
  if (length(subs) == 0){
    return(NULL)
  } else {
    return(subs) 
  }
})
null_bool <- map(psp_kin_sub_list_relevant_trim, ~!is.null(.)) %>% unlist
psp_kin_sub_list_relevant_trim <- psp_kin_sub_list_relevant_trim[null_bool]

##Run enrichment
#Bkd: Entire ppome
kinase_enr_compr_df <- clust_enricher(clust_genes = WGCNA_clusters_SGIDs,
                                      bkd_genes = unique(phos_data_annotation$SITE_GRP_ID),
                                      pways_list = psp_kin_sub_list_relevant_trim)
```

Visualise
```{r}
###Heatmap of kinases
overrep_hmap(kinase_enr_compr_df)
ggsave_pdfpng("output/images/analysis/corr_network/WGCNA/kinases/hmap_WGCNA_kin_overrep",
              width = 4, height = 2)
overrep_hmap(kinase_enr_compr_df,
             scale_colours_manually = TRUE,
             mid_colour_threshold = 3,
             high_colour_threshold = 6.7)
ggsave_pdfpng("output/images/analysis/corr_network/WGCNA/kinases/hmap_WGCNA_kin_overrep_samescale",
              width = 4, height = 2)
```

###SH 2013 temporal clusters
Process data
```{r}
###Load in SH data
library(readxl)
SH_rawest <- read_xlsx("data/intermediate/biol_databases/supplementary_tables/Sean Cell Metab 2013/sean_cell_metab_2013_mmc4.xlsx")
SH_raw <- SH_rawest %>%
  rename("Gene Name" = "gene",
         "Phosphorylated Amino Acid" = "AA",
         "IPI 3.68 Position in Protein" = "position",
         "Sequence Window" = "sequence_window")

###Prep insreg data
load("data/intermediate/phos_data/phos_data_proc_insreg__4.RData")
##Make truncated sequence window for GxE ppome
phos_data_proc_insreg$sequence_window_trunc <- strsplit(phos_data_proc_insreg$sequence_window, "") %>%
  map(~paste(.[10:22], collapse = "")) %>% unlist
##Insreg data
GxE_insreg <- subset(phos_data_proc_insreg, insreg_bool == TRUE)

###Map SH data over
##How many map into SH data by sequence_window?
#283/441
length(which(GxE_insreg$sequence_window_trunc %in% SH_raw$sequence_window))

##Get matches in SH data
insreg_matches <- map(GxE_insreg$sequence_window_trunc, ~which(SH_raw$sequence_window == .))
insreg_matches_num <- map(insreg_matches, length) %>% unlist

##Rectify multiple matches (based on my judgement of gene + site)
insreg_matches[[which(insreg_matches_num == 2)]] <- which(SH_raw$UniqueID == 
                                                            "IPI00119663_185_TGFLTEYVATRWY_Y")
insreg_matches[[which(insreg_matches_num == 3)]] <- which(SH_raw$UniqueID == 
                                                            "IPI00115040_66_SPPRSQTPQDTNR_T")

##Make df of matches
insreg_matches_df <- GxE_insreg[which(insreg_matches_num > 0), c("standard_name",
                                    "gene", "uniprot", "site", "uniprot_site",
                                    "sequence_window", "sequence_window_trunc")]
insreg_matches_df$position <- gsub("[STY]", "", insreg_matches_df$site)
colnames(insreg_matches_df) <- paste("GxE_", colnames(insreg_matches_df), sep = "")
SH_matches <- SH_raw[unlist(insreg_matches), c("gene", "AA", "position", "UniqueID", "sequence_window",
                                               "Uniprot ID")]
colnames(SH_matches) <- paste("SH_", colnames(SH_matches), sep = "")
insreg_matches_df <- cbind(insreg_matches_df, SH_matches)

##Inspect
#When do sites not match?
subset(insreg_matches_df, SH_position != GxE_position) %>% .[, c("GxE_standard_name", "SH_gene", "SH_Uniprot ID")]

#When do sites and genes not match?
site_gene_nomatch <- subset(insreg_matches_df, SH_position != GxE_position &
         SH_gene != GxE_gene) %>% .[, c("GxE_standard_name", "SH_gene", "SH_UniqueID")]
#By manual inspection, all of these cases match to different names for the same gene (genecards search)
site_gene_fixmatch <- c("Akap",
                        "Epb4.1",
                        "Nkcc1",
                        "Mkl2",
                        "Bsg4",
                        "Jip4",
                        "Atbp",
                        "Est1c",
                        "Kiaa0664",
                        "Kiaa1296",
                        "Lrrc35",
                        "Kiaa0819",
                        "Plec1",
                        "Af6",
                        "Tcfeb")
##Final mapping
GxE_insreg[, c("SH_UniqueID", "SH_cluster")] <- NA
for (i in 1:nrow(GxE_insreg)){
  match <- insreg_matches[[i]]
  if (length(match) > 0){
    GxE_insreg[i, c("SH_UniqueID", "SH_cluster")] <- 
      SH_raw[match, c("UniqueID", "Cluster")]
  }
}

##Classification of different clusters
SH_cluster_info <- read_xlsx("data/intermediate/biol_databases/supplementary_tables/Sean Cell Metab 2013/sean_cell_metab_2013_clusterinfo.xlsx", sheet = "info")
#Map into GxE_insreg
clustinfo_cols <- colnames(SH_cluster_info)[-1]
GxE_insreg[, paste("SH_", clustinfo_cols, sep = "")] <- NA
for (i in 1:nrow(GxE_insreg)){
  SH_clust <- GxE_insreg$SH_cluster[i]
  if (!is.na(SH_clust)){
    GxE_insreg[i, paste("SH_", clustinfo_cols, sep = "")] <-
      SH_cluster_info[which(SH_cluster_info$cluster == SH_clust), clustinfo_cols]
  }
}

insreg_data_SHmapped <- GxE_insreg
```


Visualise
```{r}
###Summary of peak speed in each cluster
##Prep data
#Add WGCNA cluster to data
insreg_data_SHmapped$WGCNA_cluster <- factor(WGCNA_net$colors[rownames(insreg_data_SHmapped)],
                                             levels = sort(unique(WGCNA_net$colors)))
#Turn speed into factor
insreg_data_SHmapped$SH_peak_time <- factor(insreg_data_SHmapped$SH_peak_time,
                                            levels = sort(unique(insreg_data_SHmapped$SH_peak_time)))

##Pairwise summary of WGCNA cluster and peak time
WGCNAclust_SHpeaktime_summary <-summariser_twoway_prop(insreg_data_SHmapped,
                       Var1 = "WGCNA_cluster",
                       Var2 = "SH_peak_time")

##Summarise number of ppeptides in each cluster
num_clust_SH <- subset(insreg_data_SHmapped, !is.na(SH_peak_time)) %>% .$WGCNA_cluster %>% table
num_clust <- table(WGCNA_net$colors)

num_clust_SH/num_clust

sum(num_clust_SH[-1])
sum(table(WGCNA_net$colors)[-1])


##Plot
#Proportion
ggplot(WGCNAclust_SHpeaktime_summary,
       aes(x = WGCNA_cluster, y = prop_of_WGCNA_cluster*100,
           fill = SH_peak_time)) +
  geom_col() +
  scale_fill_manual(values = brewer.pal(7, "Reds"),
                    name = "Peak time (min)") +
  comfy_theme(include_xaxis = FALSE) +
  labs(x = "Cluster", y = "% of phosphopeptides in cluster")
ggsave_pdfpng("output/images/analysis/corr_network/WGCNA/SH_2013/barplot_WGCNAclust_SHpeaktime_prop",
              width = 3, height = 2)
#Frequency
ggplot(WGCNAclust_SHpeaktime_summary,
       aes(x = WGCNA_cluster, y = Freq,
           fill = SH_peak_time)) +
  geom_col() +
  scale_fill_manual(values = brewer.pal(7, "Reds"),
                    name = "Peak time (min)") +
  comfy_theme(include_xaxis = FALSE) +
  labs(x = "Cluster", y = "Phosphopeptides")
ggsave_pdfpng("output/images/analysis/corr_network/WGCNA/SH_2013/barplot_WGCNAclust_SHpeaktime_Freq",
              width = 3, height = 2)
```






####Eigenpeptide analysis
Here I look at the module eigengenes, which I term "eigenpeptides"

Initial preparation and visualisation
```{r}
###Prepare eigenpeptide data
##Extract eigenpeptides
WGCNA_eigenpeptides <- WGCNA_net$MEs %>%
  .[, order(colnames(.))] %>% .[, -1]
colnames(WGCNA_eigenpeptides) <- gsub("ME", "", colnames(WGCNA_eigenpeptides)) %>%
  paste(., "_eigenpept", sep = "")
WGCNA_eigenpeptides <- t(WGCNA_eigenpeptides) %>% as.data.frame
##StrainDiet medians
num_data <- WGCNA_eigenpeptides[, grep("basnorm_\\d+$", colnames(WGCNA_eigenpeptides))]
StrainDiet_medians <- map(all_levels$StrainDiet, function(strain_diet){
  apply(num_data[, grep(strain_diet, colnames(num_data))],
      1, FUN = "median", na.rm = TRUE)
}) %>% purrr::reduce(cbind) %>% as.data.frame
colnames(StrainDiet_medians) <- map(all_levels$StrainDiet, 
                                    ~paste(., "_bas_vs_", ., "_ins_logFC", sep = "")) %>% unlist
WGCNA_eigenpeptides <- cbind(WGCNA_eigenpeptides, StrainDiet_medians)





###Visualise
##Stacked lines
##Prep data
eigenpep_FC_long <- WGCNA_eigenpeptides %>%
  .[, grep("logFC$", colnames(.))] %>%
  mutate(cluster = strsplit(rownames(.), "_") %>% map(~.[1]) %>% unlist) %>%
  pivot_longer(cols = colnames(.)[grep("logFC$", colnames(.))],
               names_to = "FC_col", values_to = "val") %>%
  mutate(strain_diet = factor(gsub("_bas_.+", "", FC_col),
                              levels = all_levels$StrainDiet))

##Plot
ggplot(eigenpep_FC_long, 
       aes(x = strain_diet, y = val, group = cluster, colour = cluster)) +
  #geoms
  geom_line(linewidth = 0.235) +
  geom_point(size = 0.5, shape = 16) +
  #Themes
  scale_colour_manual(values = cluster_colours) +
  comfy_theme(include_xaxis = FALSE, rotate_x_text = TRUE,
              include_legend = FALSE) +
  theme(axis.title.x = element_blank()) +
  labs(y = "Relative insulin response") +
  #Facet
  facet_wrap(facets = vars(cluster), ncol = 1,
             strip.position = "left")
ggsave_pdfpng(file = "output/images/analysis/corr_network/WGCNA/eigenpeptides/lplot_eigenpept_insresp",
              width = 2, height = 3)
```





Correlate with glucose uptake
```{r}
##Load in and combine data
source("scripts/10_GU_correlations.R")
load("data/intermediate/pheno_data/pheno_data__5.RData")

eigenpept_GU_df <- combine_phos_pheno_data(phos_data = WGCNA_eigenpeptides,
                        pheno_data = pheno_data,
                        pheno_cols = c("sol_p2DG_weightnorm_rate"),
                        phos_rows = rownames(WGCNA_eigenpeptides),
                        phos_num_cols = basnorm_cols,
                        phos_UIDs = gsub("basnorm_", "", basnorm_cols))
##Run correlations
eigenpept_GU_corr <- phos_GU_correlator_mult_fromcomb(eigenpept_GU_df, 
                                                     ppeptides =rownames(WGCNA_eigenpeptides),
                                                     cor_method = "pearson")

###Visualise
##Barplot of correlations
eigenpept_GU_corr <- mutate(eigenpept_GU_corr,
                            cor_p_nlog10 = -log10(cor_p),
                            cluster = strsplit(rownames(eigenpept_GU_corr), "_") %>% 
                              map(~.[1]) %>% unlist)
eigenpept_GU_corr <- eigenpept_GU_corr %>% .[order(.$cor_r), ] %>%
  mutate(cluster = factor(cluster, levels = unique(cluster)))
#Plot
ggplot(eigenpept_GU_corr, aes(x = cor_r, y = cluster, fill = cor_p_nlog10)) +
  geom_col() +
  geom_vline(xintercept = 0,
             size = 0.235, colour = "black") +
  comfy_theme(include_yaxis = FALSE) +
  scale_fill_gradientn(colors = c("#e6efe6", "#69af69", "#2c752c"),
                       values = rescale(c(0, 0.5*max(eigenpept_GU_corr$cor_p_nlog10),
                                          max(eigenpept_GU_corr$cor_p_nlog10))),
                       limits = c(0, max(eigenpept_GU_corr$cor_p_nlog10)),
                          name = "-log10 p-value") +
  labs(x = "r", y = "Cluster")
ggsave_pdfpng("output/images/analysis/corr_network/WGCNA/eigenpeptides/bplot_eigenpep_GU_corr",
              width = 2.75, height = 1.4)
```



####Central ppeptides / module membership by eigengene correlation
```{r}
###Set up
##Get module memberships
MM_matrix <- cor(data_preWGCNA, t(WGCNA_eigenpeptides[, basnorm_cols]),
    use = "pairwise.complete.obs")
##Function to extract module memberships
get_cluster_MMs <- function(cluster){
  cluster <- as.character(cluster)
  MM_cluster <- MM_matrix[WGCNA_clusters[[cluster]], 
                          paste(cluster, "_eigenpept", sep = "")]
  MM_cluster <- MM_cluster[order(abs(MM_cluster), decreasing = TRUE)]
  return(MM_cluster)
}

###Make a summary
clusters_GU_corr <- strsplit(rownames(eigenpept_GU_corr), "_") %>% map(~.[1]) %>% unlist
clusters_GU_MM <- map(clusters_GU_corr, function(clust){
  MM_cluster <- get_cluster_MMs(clust)
  MM_cluster_df <- data.frame("cluster" = clust, "MM" = MM_cluster)
}) %>% purrr::reduce(rbind)
##Add GU corrs
load("data/intermediate/phos_data/GU_corrs/insreg_corrs_results.RData")
clusters_GU_MM[, colnames(insreg_corrs_results$insresp)] <- 
  insreg_corrs_results$insresp[rownames(clusters_GU_MM), ]
##Add annotation
clusters_GU_MM <- annotation_search_mapback(clusters_GU_MM)


###Export
write.csv(clusters_GU_MM, file = "output/data/analysis/WGCNA/WGCNA_cluster_summary.csv")
```


#####Enrichment on ranked module membership
I use ppeptide-eigengene correlation as a measure of module membership
I perform pathway enrichment on the ranks of these correlations

Set up rank matrix
```{r}
MM_matrix_abs <- abs(MM_matrix)
MM_matrix_rank <- MM_matrix_abs
MM_matrix_genes <- strsplit(rownames(MM_matrix_abs), "_") %>% map(~.[1]) %>% unlist
for (j in 1:ncol(MM_matrix_abs)){
  vec <- MM_matrix_abs[, j]
  vec <- sort(vec, decreasing = TRUE)
  MM_matrix_rank[names(vec), j] <- 1:length(vec)
}
```


GO enrichment
```{r}
###Get GO pathways lists
relevant_GOIDs_gst <- map(c("BP" = "BP", "CC" = "CC"), function(ont){
  relevant_GOIDs_list <- relevant_GOIDS(DE_genes = unique(unlist(WGCNA_clusters_genes)),
                                        gene_label = "SYMBOL",
                                        organism_database = org.Mm.eg.db,
                                        ontology = ont)
  #Rename using GO term
  GO_terms <- AnnotationDbi::select(GO.db,
                                   names(relevant_GOIDs_list),
                                   columns = "TERM",
                                   keytype = "GOID")$TERM
  names(relevant_GOIDs_list) <- GO_terms
     return(relevant_GOIDs_list)
})


###Run enrichment
GO_GST_res <- map(relevant_GOIDs_gst, function(pwayLst){
  #Run enrichment
  GO_GST <- map(1:ncol(MM_matrix_abs), function(j){
    cluster <- gsub("_eigenpept", "", colnames(MM_matrix_abs)[j])
    enr <- gst_enricher(pathways_list = pwayLst,
                        stats = MM_matrix_abs[, j],
                        stats_genes = MM_matrix_genes,
                        alternative = "greater",
                        type = "t",
                        background_pathway_intersection_threshold = 3,
                        intersection_as_unique = TRUE)
    colnames(enr) <- paste(cluster, colnames(enr), sep = "_")
    return(enr)
  })
  #Combine into one df
  common_rows <- rownames(GO_GST[[1]])
  GO_GST_df <- map(GO_GST, ~.[common_rows, ]) %>% purrr::reduce(cbind) %>% as.data.frame
  return(GO_GST_df)
})


###Inspect results
##Num significant (after adjustment in each column)
map(GO_GST_res, ~colSums(.[, grep("adj_pval$", colnames(.))] < 0.05))
#No adjustment
map(GO_GST_res, ~colSums(.[, grep("^[1-8]_pval$", colnames(.))] < 0.01))

##Significant at unadjusted p < 0.01:
map(GO_GST_res, function(enr){
  for (j in 1:8){
    print(j)
    print(rownames(enr)[which(enr[, paste(j, "_pval", sep = "")] < 0.01)])
  }
})


###Visualise
GO_dir <- "output/images/analysis/corr_network/WGCNA/GO/rank/hmap_WGCNA_GOgst_"
overrep_hmap_pval(data = GO_GST_res$BP,
                  sig_threshold = 0.01,
                  pcol_suffix = "^[0-9]_pval$",
                  conditions = 1:8) +
  ggtitle("GO Biological Processes")
ggsave_pdfpng(paste(GO_dir, "BP", sep = ""),
              width = 5.5, height = 3.5)
overrep_hmap_pval(data = GO_GST_res$CC,
                  sig_threshold = 0.01,
                  pcol_suffix = "^[0-9]_pval$",
                  conditions = 1:8) +
  ggtitle("GO Cellular Comartments")
ggsave_pdfpng(paste(GO_dir, "CC", sep = ""),
              width = 5.5, height = 3.5)
```

Kinase enrichment
```{r}
###Get SITE_GRP_IDs for membership matrix
MM_matrix_abs_SGIDs <- phos_data_annotation[rownames(MM_matrix_abs), "PSP_SITE_GRP_ID"]

###Get kinase list
load("data/intermediate/biol_databases/psp_kin_sub_list_invivo_noauto_Gsk3i__1.RData")
##Remove promiscuous psites. promisc_threshold = 4 was used for KSEA
SGIDs <- unique(MM_matrix_abs_SGIDs)
promisc_bool <- promisc_psites_trim(stat_names = SGIDs,
                                    kin_sub_list = psp_kin_sub_list_invivo_noauto_Gsk3i,
                                    promisc_threshold = 4)
promisc_SGIDs <- SGIDs[!promisc_bool]
#Remove from kinase sub list
psp_kin_sub_list_trim <- map(psp_kin_sub_list_invivo_noauto_Gsk3i, function(subs){
  subs <- subs[which(subs %in% promisc_SGIDs == FALSE)]
  if (length(subs) == 0){
    return(NULL)
  } else {
    return(subs) 
  }
})
null_bool <- map(psp_kin_sub_list_trim, ~!is.null(.)) %>% unlist
psp_kin_sub_list_trim <- psp_kin_sub_list_trim[null_bool]

###Run enrichment
kin_GST_res <- map(1:ncol(MM_matrix_abs), function(j){
  cluster <- gsub("_eigenpept", "", colnames(MM_matrix_abs)[j])
  enr <- gst_enricher(pathways_list = psp_kin_sub_list_trim,
                      stats = MM_matrix_abs[, j],
                      stats_genes = MM_matrix_abs_SGIDs,
                      alternative = "greater",
                      type = "t",
                      background_pathway_intersection_threshold = 3,
                      intersection_as_unique = TRUE)
  colnames(enr) <- paste(cluster, colnames(enr), sep = "_")
  return(enr)
})
#Combine into one df
common_rows <- rownames(kin_GST_res[[1]])
kin_GST_df <- map(kin_GST_res, ~.[common_rows, ]) %>% purrr::reduce(cbind) %>% as.data.frame


###Inspect results
##Num significant (after adjustment in each column)
colSums(kin_GST_df[, grep("adj_pval$", colnames(kin_GST_df))] < 0.05)
#No adjustment
colSums(kin_GST_df[, grep("^[1-8]_pval$", colnames(kin_GST_df))] < 0.05)

##Significant at unadjusted p < 0.01:
for (j in 1:8){
  print(j)
  print(rownames(kin_GST_df)[which(kin_GST_df[, paste(j, "_pval", sep = "")] < 0.05)])
}
overrep_hmap_pval(data = kin_GST_df,
                  sig_threshold = 0.05,
                  pcol_suffix = "^[0-9]_pval$",
                  conditions = 1:8) +
  ggtitle("Kinase substrates")
ggsave_pdfpng("output/images/analysis/corr_network/WGCNA/kinases/rank/hmap_WGCNA_kinGST",
              width = 4.5, height = 3)
```



#####Module membership for GU-correlated ppeptides
```{r}
###Set up membership for GU-correlated ppeptides
load("data/intermediate/phos_data/GU_corrs/insreg_corrs_results.RData") #Load in GU correlations
MM_matrix_abs_GUcorr <- map(insreg_corrs_results, function(dat){ #Set up module membership
  mat <- MM_matrix_abs[rownames(subset(dat, correlated == TRUE)), ] %>%
    as.data.frame
  return(mat)
})

###Visualise
##Heatmaps
fc_sig_heatmap(MM_matrix_abs_GUcorr$insresp,
               fc_cols_wo_pvals = paste(1:8, "eigenpept", sep = "_"),
               x_axis_names = 1:8,
               clust_cols = paste(1:8, "eigenpept", sep = "_"),
               legend_title = "Module membership",
               scale_colours_manually = T,
               mid_colour_threshold = 0.55,
               high_colour_threshold = 1) +
  ggtitle("Insulin response-correlated phosphopeptides")
ggsave_pdfpng(file = "output/images/analysis/corr_network/WGCNA/GU_corr/hmap_moduleMemb_insrespcorr",
              width = 4, height = 3)
fc_sig_heatmap(MM_matrix_abs_GUcorr$absint,
               fc_cols_wo_pvals = paste(1:8, "eigenpept", sep = "_"),
               x_axis_names = 1:8,
               clust_cols = paste(1:8, "eigenpept", sep = "_"),
               legend_title = "Module membership",
               scale_colours_manually = T,
               mid_colour_threshold = 0.55,
               high_colour_threshold = 1) +
  ggtitle("Insulin-stimulated intensity-correlated phosphopeptides")
ggsave_pdfpng(file = "output/images/analysis/corr_network/WGCNA/GU_corr/hmap_moduleMemb_absintcorr",
              width = 4, height = 5)
```



#####Strain and Diet tests on eigenpeptides
Set up
```{r}
phos_num_cols_basnorm <- colnames(phos_data_proc_insreg)[grep("basnorm_\\d+", 
                                                              colnames(phos_data_proc_insreg))]

source("scripts/08_ins_reg.R")
```

Strain effects
```{r}
##Run ANOVAs
data_CHOWaov <- ppeptide_stat_runner(WGCNA_eigenpeptides,
                                 num_cols = phos_num_cols_basnorm[grep("CHOW", phos_num_cols_basnorm)],
                                 test_func = strain_CHOW_aov,
                                 results_format = c("p", "F"))
#Adjust pvals
data_CHOWaov$q <- p.adjust(data_CHOWaov$p, method = "fdr")
data_CHOWaov$sig <- data_CHOWaov$q < 0.05
colnames(data_CHOWaov) <- paste("Strainaov_", colnames(data_CHOWaov), sep = "")

##Posthoc tests
#Set up
comparisons <- paste(all_levels$Strain[all_levels$Strain != "C57Bl6J"], "_vs_C57Bl6J", sep = "")
results_cols <- cross(list(c("p", "t"), comparisons)) %>%
  map(~paste(rev(unlist(.)), collapse = "_")) %>% unlist
test_func <- Strain_C57Bl6J_ttests
ppeptides <- rownames(subset(data_CHOWaov, Strainaov_sig == TRUE))
#Run ttests
data_CHOWaov_phoc <- ppeptide_stat_runner(WGCNA_eigenpeptides[ppeptides, ],
                             num_cols = phos_num_cols_basnorm[grep("CHOW", phos_num_cols_basnorm)],
                             test_func = test_func,
                             results_format = results_cols)
#Adjust pvalues
data_CHOWaov_phoc_adj <- p.adjust_mult_cols(data_CHOWaov_phoc, 
                                        pval_cols = colnames(data_CHOWaov_phoc) %>% .[grep("_p$", .)])
colnames(data_CHOWaov_phoc_adj) <- paste(colnames(data_CHOWaov_phoc_adj), "adj", sep = "")
data_CHOWaov_phoc_adj[, gsub("_padj$", "_sig", colnames(data_CHOWaov_phoc_adj))] <- data_CHOWaov_phoc_adj < 0.05
data_CHOWaov_phoc <- cbind(data_CHOWaov_phoc, data_CHOWaov_phoc_adj)

##Overall summary
eigenpept_Straineffect_df <- data_CHOWaov_phoc
eigenpept_Straineffect_df[setdiff(rownames(data_CHOWaov), rownames(data_CHOWaov_phoc)), ] <- NA
eigenpept_Straineffect_df[setdiff(rownames(data_CHOWaov), rownames(data_CHOWaov_phoc)), 
                           grep("_sig$", colnames(eigenpept_Straineffect_df))] <- FALSE
eigenpept_Straineffect_sum <- eigenpept_Straineffect_df %>% .[, grep("_sig$", colnames(.))]
#Stars
eigenpept_Straineffect_df %>% .[, grep("_padj$", colnames(.))] %>% ps_to_stars_df
```

Diet effects
```{r}
##Run ANOVAs
data_regdiff <- ppeptide_stat_runner(WGCNA_eigenpeptides,
                                     num_cols = phos_num_cols_basnorm,
                                     test_func = strainxdiet_aov,
                                     results_format = c("Strain_p", "Diet_p", "StrainxDiet_p",
                                                        "Strain_F", "Diet_F", "StrainxDiet_F")) %>%
  .[, -grep("Strain_", colnames(.))]
#p-value adjustment across all columns
conditions <- c("Diet", "StrainxDiet")
pcols <- paste(conditions, "_p", sep = "")
qcols <- paste(conditions, "_q", sep = "")
sig_cols <- paste(conditions, "_sig", sep = "")
#adjusted p-values
qvalues <- p.adjust_mult_cols(data_regdiff[, pcols], pval_cols = pcols, method = "fdr")
data_regdiff[, qcols] <- qvalues
#Significance
for (i in 1:length(pcols)){
  data_regdiff[, sig_cols[i]] <- FALSE
  data_regdiff[which(data_regdiff[, qcols[i]] < 0.05), sig_cols[i]] <- TRUE
}
#Make a column for which posthoc tests will be performed
#This is:
#StrainxDiet always if StrainxDiet is significant. Otherwise:
#Diet if Diet is signifciant only
#Classify each as S, D, SxD, S+D
data_regdiff$posthoc_class <- "none"
data_regdiff$posthoc_class[data_regdiff$Diet_sig] <- "Diet"
data_regdiff$posthoc_class[data_regdiff$StrainxDiet_sig] <- "StrainxDiet"
data_regdiff$posthoc_class <- factor(data_regdiff$posthoc_class,
                                     levels = c("none", "StrainxDiet", "Diet"))
data_Diet_SxDaov <- data_regdiff

##Run posthocs
diet_comparisons <- map(all_levels$Strain, ~paste(., "_HFD_vs_", ., "_CHOW", sep = "")) %>% unlist
results_cols <- cross(list(c("p", "t"), diet_comparisons)) %>%
  map(~paste(rev(unlist(.)), collapse = "_")) %>% unlist
test_func <- StrainxDiet_Diet_ttests
ppeptides <- rownames(subset(data_Diet_SxDaov, posthoc_class == "StrainxDiet"))
#Run ttests
data_Diet_SxDaov_SxDttests <- ppeptide_stat_runner(WGCNA_eigenpeptides[ppeptides, ],
                             num_cols = phos_num_cols_basnorm,
                             test_func = test_func,
                             results_format = results_cols)
#Adjust pvalues
data_Diet_SxDaov_SxDttests_adj <- p.adjust_mult_cols(data_Diet_SxDaov_SxDttests, 
                                        pval_cols = colnames(data_Diet_SxDaov_SxDttests) %>% .[grep("_p$", .)])
colnames(data_Diet_SxDaov_SxDttests_adj) <- paste(colnames(data_Diet_SxDaov_SxDttests_adj), "adj", sep = "")
data_Diet_SxDaov_SxDttests_adj[, gsub("_padj$", "_sig", colnames(data_Diet_SxDaov_SxDttests_adj))] <- data_Diet_SxDaov_SxDttests_adj < 0.05
data_Diet_SxDaov_SxDttests <- cbind(data_Diet_SxDaov_SxDttests, data_Diet_SxDaov_SxDttests_adj)

##Overall summary
eigenpept_StrainxDieteffect_df <- data_Diet_SxDaov_SxDttests
eigenpept_StrainxDieteffect_df[setdiff(rownames(data_Diet_SxDaov), rownames(data_Diet_SxDaov_SxDttests)), ] <- NA
eigenpept_StrainxDieteffect_df[setdiff(rownames(data_Diet_SxDaov), rownames(data_Diet_SxDaov_SxDttests)), 
                           grep("_sig$", colnames(eigenpept_StrainxDieteffect_df))] <- FALSE
eigenpept_StrainxDieteffect_sum <- eigenpept_StrainxDieteffect_df %>% .[, grep("_sig$", colnames(.))]
eigenpept_StrainxDieteffect_sum <- eigenpept_StrainxDieteffect_sum[order(rownames(eigenpept_StrainxDieteffect_sum)), ]
#Stars
eigenpept_StrainxDieteffect_df %>% .[, grep("_padj$", colnames(.))] %>% ps_to_stars_df
```
















